### 2014-07-22 paper.tex
Bare bones paper

\documentclass[10pt,final,journal]{IEEEtran}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

\title{Streaming Cell Based Energy Harvester}

\author{Mark~H.~Jones,~\IEEEmembership{Student Member,~IEEE,}
~and Prof.~Jonathan~Scott,~\IEEEmembership{Senior Member,~IEEE}}

\begin{document}
    \maketitle

    \begin{abstract}

    \end{abstract}

    \section{Introduction}
\end{document}

### 2014-07-29 paper.tex
Updating references

@@
 
-\title{Streaming Cell Based Energy Harvester}
+\title{Feasibility of Harvesting Power To Run A Domestic Water Meter Using Streaming Cell Technology}
 
-\author{Mark~H.~Jones,~\IEEEmembership{Student Member,~IEEE,}
-~and Prof.~Jonathan~Scott,~\IEEEmembership{Senior Member,~IEEE}}
+\author{Mark~H.~Jones, and Prof.~Jonathan~Scott}
 
@@
     \begin{abstract}
-
+        We investigate the possibility of using streaming cells as a means of harvesting energy from potable water.
+        We fabricate a number of crude streaming potential cells, each with differing geometry.
+        We measure the electrical power developed from each of these cells over a range of pressure differentials.
+        We estimate the amount of energy required to operate a simple data logger and a typical domestic water flow profile.
+        Based on this data we calculate the size of a streaming cell harvester required to log domestic water consumption.
     \end{abstract}
@@
     \section{Introduction}
+    Domestic and commercial water metering is becoming increasingly important throughout the world as water.
+    There are two methods available to water utility companies when recording the volume of water delivered to consumers.
+    \begin{enumerate}
+        \item \emph{Mechanical readout:}
+            This involves having a human sight the meter's readout from time to time.
+            Generally the reading frequency is kept to a minimum and estimate readings are made in the interim.
+        \item \emph{Electronic telemetry:}
+            Wireless data transmission commonly used as the method of data transport.
+            Due to the location of water metering, electrical power is provided by long life batteries.
+            These batteries are usually non-rechargeable and therefore must be replaced once exhausted.
+        \end{enumerate}
+    Having a cheap and reliable way to retrieve metering information is the most important factor for utility companies.
+    The methods previously mentioned are costly to the utility as they require periodic human intervention.
+    The possibility of harvesting energy at the meter will allow periodic data transmission with less maintenance.
+    Removing batteries from electrical meters also reduces unwanted electrical waste.
+
+    Streaming cells are commonly used in membrane science to determine the zeta potential of a membrane surface.
+    This is an important factor in the design and operation of membrane based processes. \cite{Daiguji2004b}
+    Streaming cells have also been investigated as a means of pumping water and generating power.\cite{Daiguji2004b, Davidson2008, Hon2004, Olthuis2005}
+
+    In \cite{CherngHon2012}, salinity gradients are shown to produce electrical power
+
+    \bibliographystyle{plain}
+    \bibliography{library}
+
+%\begin{thebibliography}{99}
+%
+%    \bibitem{CherngHon2012}
+%    Kar~Cherng~Hon, Cunlu~Zhao, Chun~Yang, and Seow~Chay Low,
+%    ``A method of producing electrokinetic power through forward osmosis'',
+%    Appl. Phys. Lett. 101, 143902 (2012); doi: 10.1063/1.4756903
+%
+%    \bibitem{Daiguji2004b}
+%    Hirofumi~Daiguji, Peidong~Yang, Andrew~Szeri, and Arun~Majumdar,
+%    ``Electrochemomechanical Energy Conversion in Nanofluidic Channels'',
+%    Nano Letters, 2004, vol. 4, 12, pp2315-2321
+%
+%    \bibitem{Davidson2008}
+%    Christian~Davidson, Xiangchun~Xuan,
+%    ``Effects of Stern layer conductance on electrokinetic energy conversion in nanofluidic channels'',
+%    Electrophoresis-NEEDS-CHECKING
+%
+%    \bititem{Hon2012}
+%    K.C.~Hon, C.~Zhao, C.~Yang, and S.C.~Low,
+%    ``A method of producing electrokinetic power through forward osmosis'',
+%    referenceTODO
+%
+%
+%    \bibitem{Olthuis2005}
+%    Authors,
+%    ``Energy from streaming current and potential'',
+%    journal
+%
+%    \bibitem{XuanLi2006}
+%    Authors,
+%    ``Thermodynamic analysis of electrkinetic energy converson'',
+%    journal
+%
+%    \bibitem{RenStein2008}
+%    Authors,
+%    ``Slip-enhanced electrokinetic energy conversion in nanofluidic channels'',
+%    journal
+%
+%    \bibitem{vanderHeyden2006}
+%    Authors,
+%    ``Electrokinetic energy conversion efficiency in nanofluidic channels'',
+%    journal
+%
+%    \bibitem{DavidsonXuan2008b}
+%    Authors,
+%    ``Electrokinetic energy conversion in slip nanochannels'',
+%    journal
+%
+%    \bibitem{Yang2003}
+%    Authors,
+%    ``Electrokinetic microchannel battery by means of electrokinetic and microfluidic phenomena'',
+%    journal
+%
+%    \bibitem{vanderHeyden2007}
+%    Authors,
+%    ``Power Generation by Pressure-Driven Transport of Ions in Nanofluidic Channels'',
+%    journal
+%
+%    \bibitem{Xie2008}
+%    Authors,
+%    ``Electric energy generation in single track-etched nanopores'',
+%    journal
+%
+%    \bibitem{Daiguji2006}
+%    Authors,
+%    ``Theoretical studi on the efficiency of nanofluidic batteries
+%
+%
+%\end{thebibliography}
+
 \end{document}

### 2014-07-30 paper.tex
Added references and finished writing conclusion

@@
     This is an important factor in the design and operation of membrane based processes. \cite{Daiguji2004b}
-    Streaming cells have also been investigated as a means of pumping water and generating power.\cite{Daiguji2004b, Davidson2008, Hon2004, Olthuis2005}
+    A streaming cell contains one or more narrow channels (sometimes a porous material is used as the channel) across which a pressure gradient is applied.
+    The application of a pressure gradient across the cell forces fluid through the cell and causes a streaming current, which in turn, creates voltage differential across the cell.
+    This voltage differential is called the streaming potential.
 
-    In \cite{CherngHon2012}, salinity gradients are shown to produce electrical power
+    Streaming currents have been heavily investigated as a means of generating electrical energy from pressure gradients.
+\cite{Chang2009,Daiguji2006,Daiguji2004b,Davidson2008a,Davidson2008,CherngHon2012,Jiao2014,Lu2006,Olthuis2005,Osterle1964,Pennathur2007,Ren2008a,VanderHeyden2006,Heyden2007,Xie2008,Yang2003}
+    Theoretical predictions of the efficiency of standard micro/nano-fluidic channels are 2\% for pure water and 7\% for sodium chloride. \cite{VanderHeyden2006}
 
+    Experimental results show conversion efficiencies in the range of:
+    \begin{itemize}
+        \item 0.01\% by forcing water through porous glass with pore sizes from 10--16\thinspace$\mu m$.\cite{Yang2003}
+        \item 0.8\% by forcing pure water through a ceramic rod populated with 6\thinspace$\mu m$ pores. \cite{Yang2004}
+        \item 3\% by forcing sodium chloride solution through a 75\thinspace$nm$ by 50\thinspace$\mu m$ silica channel. \cite{Heyden2007}
+        \item 0.77\% by forcing sodium chloride through a 200\thinspace$nm$ pore in an alumina membrane. \cite{Lu2006}
+        \item 5\% by forcing sodium chloride solution through a 0.5\thinspace$nm$ cylindrical pore in polyethylene terephalate foil. \cite{Xie2008}
+    \end{itemize}
+
+    Techniques to induce hydrodynamic slip at the fluid-solid interface are predicted to increase this efficiency to 30-40\%. \cite{Davidson2008a, Ren2008a}
+    However, experimental results utilising slip enhanced channels have not yet been reported in the literature.
+    In \cite{Joly2006} it is suggested that a polarised hydrophobic surface would strongly enhance electro-osmotic effects and therefore further increase conversion efficiency.
+    Hydrophobic channels have not been considered due to the exotic materials required to build them.
+
+    We address the question of whether it is feasible to build a harvester using currently available materials.
+    Such a harvester must produce enough energy to operate a microprocessor and radio communication device.
+    It must collect all of its energy from a domestic water supply and be reliable.
+
+    The remainder of this work is presented as follows.
+    In section \ref{sect:streamingCell} we build and measure a simple streaming potential cell.
+    We confirm the relationship between pressure and applied pressure and investigate the effect of channel height.
+    In section \ref{sect:waterConsumption} we estimate a typical domestic water usage profile.
+    This consumption profile will be used as the basis for estimating the amount of energy available to the harvester.
+    Section \ref{sect:powerRequirements} determines the amount of energy an electronic meter would need to be useful.
+    Following on this, section \ref{sect:harvesterSize} presents the required dimensions a usable harvester would need.
+    And finally, we discuss the findings in the conclusion.
+
+    \section{Readily Attainable Streaming Cell Power}
+    \label{sect:streamingCell}
+    \section{Estimation of Typical Household Water Consumption}
+    \label{sect:waterConsumption}
+    \section{Estimation of Power Requirements}
+    \label{sect:powerRequirements}
+    \section{Estimation of Streaming Cell Harvester}
+    \label{sect:harvesterSize}
+    \section{Conclusion}
     \bibliographystyle{plain}
@@
 
-%\begin{thebibliography}{99}
-%
-%    \bibitem{CherngHon2012}
-%    Kar~Cherng~Hon, Cunlu~Zhao, Chun~Yang, and Seow~Chay Low,
-%    ``A method of producing electrokinetic power through forward osmosis'',
-%    Appl. Phys. Lett. 101, 143902 (2012); doi: 10.1063/1.4756903
-%
-%    \bibitem{Daiguji2004b}
-%    Hirofumi~Daiguji, Peidong~Yang, Andrew~Szeri, and Arun~Majumdar,
-%    ``Electrochemomechanical Energy Conversion in Nanofluidic Channels'',
-%    Nano Letters, 2004, vol. 4, 12, pp2315-2321
-%
-%    \bibitem{Davidson2008}
-%    Christian~Davidson, Xiangchun~Xuan,
-%    ``Effects of Stern layer conductance on electrokinetic energy conversion in nanofluidic channels'',
-%    Electrophoresis-NEEDS-CHECKING
-%
-%    \bititem{Hon2012}
-%    K.C.~Hon, C.~Zhao, C.~Yang, and S.C.~Low,
-%    ``A method of producing electrokinetic power through forward osmosis'',
-%    referenceTODO
-%
-%
-%    \bibitem{Olthuis2005}
-%    Authors,
-%    ``Energy from streaming current and potential'',
-%    journal
-%
-%    \bibitem{XuanLi2006}
-%    Authors,
-%    ``Thermodynamic analysis of electrkinetic energy converson'',
-%    journal
-%
-%    \bibitem{RenStein2008}
-%    Authors,
-%    ``Slip-enhanced electrokinetic energy conversion in nanofluidic channels'',
-%    journal
-%
-%    \bibitem{vanderHeyden2006}
-%    Authors,
-%    ``Electrokinetic energy conversion efficiency in nanofluidic channels'',
-%    journal
-%
-%    \bibitem{DavidsonXuan2008b}
-%    Authors,
-%    ``Electrokinetic energy conversion in slip nanochannels'',
-%    journal
-%
-%    \bibitem{Yang2003}
-%    Authors,
-%    ``Electrokinetic microchannel battery by means of electrokinetic and microfluidic phenomena'',
-%    journal
-%
-%    \bibitem{vanderHeyden2007}
-%    Authors,
-%    ``Power Generation by Pressure-Driven Transport of Ions in Nanofluidic Channels'',
-%    journal
-%
-%    \bibitem{Xie2008}
-%    Authors,
-%    ``Electric energy generation in single track-etched nanopores'',
-%    journal
-%
-%    \bibitem{Daiguji2006}
-%    Authors,
-%    ``Theoretical studi on the efficiency of nanofluidic batteries
-%
-%
-%\end{thebibliography}
-
 \end{document}

### 2014-07-31 paper.tex
Started discussion of experimental work

@@
 \usepackage{graphicx}
-
+\usepackage{siunitx}
 \title{Feasibility of Harvesting Power To Run A Domestic Water Meter Using Streaming Cell Technology}
@@
     Streaming cells are commonly used in membrane science to determine the zeta potential of a membrane surface.
-    This is an important factor in the design and operation of membrane based processes. \cite{Daiguji2004b}
+    This is an important factor in the design and operation of membrane based processes.\cite{Daiguji2004b}
     A streaming cell contains one or more narrow channels (sometimes a porous material is used as the channel) across which a pressure gradient is applied.
@@
     \cite{Chang2009,Daiguji2006,Daiguji2004b,Davidson2008a,Davidson2008,CherngHon2012,Jiao2014,Lu2006,Olthuis2005,Osterle1964,Pennathur2007,Ren2008a,VanderHeyden2006,Heyden2007,Xie2008,Yang2003}
-    Theoretical predictions of the efficiency of standard micro/nano-fluidic channels are 2\% for pure water and 7\% for sodium chloride. \cite{VanderHeyden2006}
+    Theoretical predictions of the efficiency of standard micro/nano-fluidic channels are 2\% for pure water and 7\% for sodium chloride.
+    \cite{VanderHeyden2006}
 
@@
     \begin{itemize}
-        \item 0.01\% by forcing water through porous glass with pore sizes from 10--16\thinspace$\mu m$.\cite{Yang2003}
-        \item 0.8\% by forcing pure water through a ceramic rod populated with 6\thinspace$\mu m$ pores. \cite{Yang2004}
-        \item 3\% by forcing sodium chloride solution through a 75\thinspace$nm$ by 50\thinspace$\mu m$ silica channel. \cite{Heyden2007}
-        \item 0.77\% by forcing sodium chloride through a 200\thinspace$nm$ pore in an alumina membrane. \cite{Lu2006}
-        \item 5\% by forcing sodium chloride solution through a 0.5\thinspace$nm$ cylindrical pore in polyethylene terephalate foil. \cite{Xie2008}
+        \item 0.01\% by forcing water through porous glass with pore sizes from 10\thinspace--\SI{16}{\micro\metre}.\cite{Yang2003}
+        \item 0.8\% by forcing pure water through a ceramic rod populated with \SI{6}{\micro\metre} pores. \cite{Yang2004}
+        \item 3\% by forcing sodium chloride solution through a \SI{75}{\nano\metre} by \SI{50}{\micro\metre} silica channel. \cite{Heyden2007}
+        \item 0.77\% by forcing sodium chloride through a \SI{200}{\nano\metre} pore in an alumina membrane. \cite{Lu2006}
+        \item 5\% by forcing sodium chloride solution through a \SI{0.5}{\nano\metre} cylindrical pore in polyethylene terephalate foil. \cite{Xie2008}
     \end{itemize}
@@
     Following on this, section \ref{sect:harvesterSize} presents the required dimensions a usable harvester would need.
-    And finally, we discuss the findings in the conclusion.
+    Finally we discuss the feasibility of using  in the conclusion.
 
-    \section{Readily Attainable Streaming Cell Power}
-    \label{sect:streamingCell}
+    \section{Readily Attainable Streaming Cell Power} \label{sect:streamingCell}
+    In \cite{Gu2000}, the authors use a relatively simple parallel plate design to generate streaming potentials.
+    Sandwiching plastic shims between plates of glass provided a simple way set the channel height.
+    Using this technique, the authors of \cite{Gu2000} fabricated three cells with channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
+    Each of the channels were \SI{3}{\centi\metre} long and had a inner width of \SI{1}{\centi\metre}.
+
+    We replicated the channel fabrication method and approximate dimensions to produce ten streaming cell channels found in \cite{Gu2000}.
+    The channel height of our fabricated cells range from \SI{25}{\micro\metre} to \SI{250}{\micro\metre}.
+    The channels have a length of \SI{3}{\centi\metre} and an internal width of \SI{1}{\centi\metre}.
+    \begin{figure}
+        \begin{center}
+        \includegraphics[width=\linewidth]{Photo_streamingPotential_Assembly_Step3.JPG}
+        \end{center}
+        \caption{One of ten constructed streaming cells mounted in an acrylic holder.
+Copper wires have been epoxied into each side to provide a means of measuring the developed potential across the cell.
+The shim is visible as the two orange strips at each side of the cell.}
+        \label{fig:cell}
+    \end{figure}
+    A photo of one of the cells is shown in Fig. \ref{fig:cell}.
+
     \section{Estimation of Typical Household Water Consumption}

### 2014-08-04 paper.tex
Minor edits

@@
 \usepackage{siunitx}
+\usepackage[usenames, dvipsnames]{color}
+
 \title{Feasibility of Harvesting Power To Run A Domestic Water Meter Using Streaming Cell Technology}
@@
     \section{Introduction}
-    Domestic and commercial water metering is becoming increasingly important throughout the world as water.
+    Domestic and commercial water metering is becoming increasingly important throughout the world.
     There are two methods available to water utility companies when recording the volume of water delivered to consumers.
@@
         \end{enumerate}
+    {[\color{blue}Suggested adding references to the above items. Not really sure what I would be adding - a specific example would be good]}
     Having a cheap and reliable way to retrieve metering information is the most important factor for utility companies.
@@
     Removing batteries from electrical meters also reduces unwanted electrical waste.
+
+    Streaming cells provide a way of converting fluid pressure/flow into electrical voltage/current.
+    When fluid comes into contact with a solid phase it is common for a difference in electrical potential to exist at the interface between the two phases.
+    This difference leads to ions in the fluid phase, those of opposite polarity to the net polarity of the solid phase (termed counter-ions), being attracted to the liquid-solid interface.
+    These counter-ions collect at the interface boundary in two layers; the Stern layer and the diffuse layer.
+    The Stern layer is comprised of immobilised counter-ions situated very close the charged solid surface. \cite{Salieb-Beugelaar2009}
+    The diffuse layer is formed by the ions attracted to the surface, but not so tightly as to be immobile.
+    A streaming cell makes use of these collected ions by forcing them through one or more narrow channels.
+
+    It is important that the channel's dimensions are such that the interior of the channel is occupied prodomonantly by counter-ions.
+
+    A streaming cell is formed by creating a channel through a solid object.
+    For the cell to be effective, the dimensions of the channel are in the order of the thickness of the formed double layer.
+
+    They are routinely used in membrane science to measure the electrical properties of of membrane based processes. \cite{Daiguji2004b}
+    {\color{blue} Suggested saying something about a body of literature relating to streaming cells - unsure of the context or relevance of that suggestion}
 
@@
     \begin{itemize}
-        \item 0.01\% by forcing water through porous glass with pore sizes from 10\thinspace--\SI{16}{\micro\metre}.\cite{Yang2003}
+        \item 0.01\% by forcing water through porous glass with pore sizes from 10\thinspace--\SI{16}{\micro\metre}. \cite{Yang2003}
         \item 0.8\% by forcing pure water through a ceramic rod populated with \SI{6}{\micro\metre} pores. \cite{Yang2004}

### 2014-08-05 paper.tex
Reworked introduction

--- 2014-07-31 paper.tex
@@
     \begin{abstract}
-        We investigate the possibility of using streaming cells as a means of harvesting energy from potable water.
-        We fabricate a number of crude streaming potential cells, each with differing geometry.
-        We measure the electrical power developed from each of these cells over a range of pressure differentials.
-        We estimate the amount of energy required to operate a simple data logger and a typical domestic water flow profile.
-        Based on this data we calculate the size of a streaming cell harvester required to log domestic water consumption.
+        We investigate the possibility of using streaming cells as a means of harvesting energy from a town water supply.
+        We verify streaming cell measurements found in the literature and extend those measurements over a wider range of dimensions.
+        We measure the electrical power developed from ten streaming cells over a range of pressure differentials using town water.
+        We estimate the amount of energy required to operate a simple data logger and transmitter.
+        We estimate the amount of energy available from a typical domestic household based on water usage data.
+        Finally, we calculate the dimensions required to build a streaming cell harvester large enough to enable domestic water consumption logging and transmission.
     \end{abstract}
@@
     \section{Introduction}
-    Domestic and commercial water metering is becoming increasingly important throughout the world as water.
+    Domestic and commercial water metering is becoming increasingly important throughout the world.
+    Having a cheap and reliable way to retrieve metering information is the most important factor for utility companies.
     There are two methods available to water utility companies when recording the volume of water delivered to consumers.
@@
         \item \emph{Mechanical readout:}
-            This involves having a human sight the meter's readout from time to time.
+            This involves having a meter-reader sight each meter's readout from time to time.
             Generally the reading frequency is kept to a minimum and estimate readings are made in the interim.
         \item \emph{Electronic telemetry:}
-            Wireless data transmission commonly used as the method of data transport.
-            Due to the location of water metering, electrical power is provided by long life batteries.
+            Wireless data transmission is increasingly becoming used as a method of metering data recovery.
+            Due to the location of water metering, electrical power must be provided by long life batteries.
             These batteries are usually non-rechargeable and therefore must be replaced once exhausted.
         \end{enumerate}
-    Having a cheap and reliable way to retrieve metering information is the most important factor for utility companies.
+    {\color{blue}[Suggested adding references to the above items. Not really sure what I would be adding - a specific example would be good]}
     The methods previously mentioned are costly to the utility as they require periodic human intervention.
@@
 
-    Streaming cells are commonly used in membrane science to determine the zeta potential of a membrane surface.
-    This is an important factor in the design and operation of membrane based processes.\cite{Daiguji2004b}
-    A streaming cell contains one or more narrow channels (sometimes a porous material is used as the channel) across which a pressure gradient is applied.
-    The application of a pressure gradient across the cell forces fluid through the cell and causes a streaming current, which in turn, creates voltage differential across the cell.
-    This voltage differential is called the streaming potential.
+    Streaming cells provide a way of converting fluid pressure/flow into electrical voltage/current.
+    Charged surfaces in contact with ionic solutions attract counter-ions\footnote{The terms counter-ion and co-ion refer to ions of opposite and like charge relative to the polarity of the solid surface respectively.} while repelling co-ions so as to form a charged layer.~\cite{Stein2004}
+    This charged layer is termed the double layer and is the key mechanism that enables streaming cell energy conversion.
 
-    Streaming currents have been heavily investigated as a means of generating electrical energy from pressure gradients.
-    \cite{Chang2009,Daiguji2006,Daiguji2004b,Davidson2008a,Davidson2008,CherngHon2012,Jiao2014,Lu2006,Olthuis2005,Osterle1964,Pennathur2007,Ren2008a,VanderHeyden2006,Heyden2007,Xie2008,Yang2003}
-    Theoretical predictions of the efficiency of standard micro/nano-fluidic channels are 2\% for pure water and 7\% for sodium chloride.
-    \cite{VanderHeyden2006}
+    A double layer can be broken into two sub-layers; the Stern and diffuse layers.
+    The Stern layer is comprised of immobilised ions situated very close the charged solid surface.~\cite{Salieb-Beugelaar2009}
+    The diffuse layer is formed by the ions attracted to the surface, but not so strongly as to be immobile.
 
+    A streaming cell makes use of ions at the interface by forcing them through one or more narrow channels.
+    The channels can be formed from porous materials or created individually by various fabrication methods, e.g. chemical etching.
+    By immersing a channel in an electrolyte solution, double layers line the interior to the channel.
+    The thickness of the double layer is represented by the Debye length ($l_{D}$) and is controlled the ionic concentration of the liquid.~\cite{Israelachvili2011}
+    When the dimensions of a channel become small enough the double layers begin to overlap and co-ions are repelled from the channel.
+
+    Counter-ions within a streaming cell are collected by applying a pressure gradient across the channel/cell.
+    Pressure forces the liquid through the channel (from which co-ions have been removed) creating a streaming current.
+    It is the streaming current that raises the voltage (streaming potential) across the cell as the ions are pumped through it.
+
+    Streaming currents have been heavily investigated as a means of generating electrical energy from pressure gradients.~\cite{Chang2009,Daiguji2006,Daiguji2004b,Davidson2008a,Davidson2008,CherngHon2012,Jiao2014,Lu2006,Olthuis2005,Osterle1964,Pennathur2007,Ren2008a,VanderHeyden2006,Heyden2007,Xie2008,Yang2003}
+    % It is expected that a channel height equal to twice the Debye length leads to maximum energy conversion efficiency.~\cite{Daiguji2004b}
+    Theoretical predictions of the efficiency of standard micro/nano-fluidic channels are 2\% for pure water and 7\% for sodium chloride.~\cite{VanderHeyden2006}
     Experimental results show conversion efficiencies in the range of:
     \begin{itemize}
-        \item 0.01\% by forcing water through porous glass with pore sizes from 10\thinspace--\SI{16}{\micro\metre}.\cite{Yang2003}
-        \item 0.8\% by forcing pure water through a ceramic rod populated with \SI{6}{\micro\metre} pores. \cite{Yang2004}
-        \item 3\% by forcing sodium chloride solution through a \SI{75}{\nano\metre} by \SI{50}{\micro\metre} silica channel. \cite{Heyden2007}
-        \item 0.77\% by forcing sodium chloride through a \SI{200}{\nano\metre} pore in an alumina membrane. \cite{Lu2006}
-        \item 5\% by forcing sodium chloride solution through a \SI{0.5}{\nano\metre} cylindrical pore in polyethylene terephalate foil. \cite{Xie2008}
+        \item 0.01\% by forcing water through porous glass with pore sizes from 10\thinspace--\SI{16}{\micro\metre}.~\cite{Yang2003}
+        \item 0.8\% by forcing pure water through a ceramic rod populated with \SI{6}{\micro\metre} pores.~\cite{Yang2004}
+        \item 3\% by forcing sodium chloride solution through a \SI{75}{\nano\metre} by \SI{50}{\micro\metre} silica channel.~\cite{Heyden2007}
+        \item 0.77\% by forcing sodium chloride through a \SI{200}{\nano\metre} pore in an alumina membrane.~\cite{Lu2006}
+        \item 5\% by forcing sodium chloride solution through a \SI{0.5}{\nano\metre} cylindrical pore in polyethylene terephalate foil.~\cite{Xie2008}
     \end{itemize}
 
-    Techniques to induce hydrodynamic slip at the fluid-solid interface are predicted to increase this efficiency to 30-40\%. \cite{Davidson2008a, Ren2008a}
+    It is clear from the literature that there is significant progress to be made with respect to increasing the conversion efficiency.
+    Techniques to induce hydrodynamic slip at the fluid-solid interface are predicted to increase this efficiency to 30-40\%.~\cite{Davidson2008a, Ren2008a}
     However, experimental results utilising slip enhanced channels have not yet been reported in the literature.
-    In \cite{Joly2006} it is suggested that a polarised hydrophobic surface would strongly enhance electro-osmotic effects and therefore further increase conversion efficiency.
+    This type of enhancement would overcome the no-slip boundary condition at the solid-liquid interface of the cavity - where ionic concentration is at its highest.
+    In~\cite{Joly2006} it is suggested that a polarised hydrophobic surface would strongly enhance electro-osmotic effects and therefore further increase conversion efficiency.
     Hydrophobic channels have not been considered due to the exotic materials required to build them.
 
-    We address the question of whether it is feasible to build a harvester using currently available materials.
+    We address the question of whether it is feasible to build a harvester using readily available materials.
     Such a harvester must produce enough energy to operate a microprocessor and radio communication device.
@@
     \section{Readily Attainable Streaming Cell Power} \label{sect:streamingCell}
-    In \cite{Gu2000}, the authors use a relatively simple parallel plate design to generate streaming potentials.
-    Sandwiching plastic shims between plates of glass provided a simple way set the channel height.
-    Using this technique, the authors of \cite{Gu2000} fabricated three cells with channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
+    In~\cite{Gu2000}, the authors employ a relatively simple parallel plate design to create a streaming cell.
+    Sandwiching plastic shims between plates of glass provided a simple way to control channel height.
+    Using that method, the authors of~\cite{Gu2000} fabricated three cells with channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
     Each of the channels were \SI{3}{\centi\metre} long and had a inner width of \SI{1}{\centi\metre}.
 
-    We replicated the channel fabrication method and approximate dimensions to produce ten streaming cell channels found in \cite{Gu2000}.
+    We replicated the channel fabrication method and approximate dimensions to produce ten streaming cell channels found in~\cite{Gu2000}.
     The channel height of our fabricated cells range from \SI{25}{\micro\metre} to \SI{250}{\micro\metre}.
-    The channels have a length of \SI{3}{\centi\metre} and an internal width of \SI{1}{\centi\metre}.
+    Our channels have a length of \SI{3}{\centi\metre} and an internal width of \SI{1}{\centi\metre}, as in~\cite{Gu2000}.
     \begin{figure}
@@
 
-    \section{Estimation of Typical Household Water Consumption}
+    \section{Estimation of Typical Household Water Consumption}:
     \label{sect:waterConsumption}

### 2014-08-06 paper.tex
Additions

@@
     Domestic and commercial water metering is becoming increasingly important throughout the world.
-    Having a cheap and reliable way to retrieve metering information is the most important factor for utility companies.
+    Having a cheap and reliable way to retrieve metering information is an important consideration for utility companies.
     There are two methods available to water utility companies when recording the volume of water delivered to consumers.
@@
         \item \emph{Mechanical readout:}
-            This involves having a meter-reader sight each meter's readout from time to time.
+            Involves a meter-reader visually sighting the meter's readout from time to time.
             Generally the reading frequency is kept to a minimum and estimate readings are made in the interim.
@@
     The methods previously mentioned are costly to the utility as they require periodic human intervention.
+    Even in the case of wireless data transmission, batteries
     The possibility of harvesting energy at the meter will allow periodic data transmission with less maintenance.
@@
 
-    We replicated the channel fabrication method and approximate dimensions to produce ten streaming cell channels found in~\cite{Gu2000}.
-    The channel height of our fabricated cells range from \SI{25}{\micro\metre} to \SI{250}{\micro\metre}.
-    Our channels have a length of \SI{3}{\centi\metre} and an internal width of \SI{1}{\centi\metre}, as in~\cite{Gu2000}.
     \begin{figure}
@@
     \end{figure}
+
+    We replicate the fabrication method and approximate dimensions of \cite{Gu2000} to produce ten streaming cell channels.
+    The internal dimensions of which are \SI{3}{\centi\metre} long, \SI{1}{\centi\metre} wide and heights in the range of \SI{25}{\micro\metre} to \SI{250}{\micro\metre}.
+    These dimensions are directly comparable to those of \cite{Gu2000}, where the length and width are the same but the heights span a wider range.
+    The channels themselves are made from glass microscope slides (Sail Brand - JIA 7101WT) which are sectioned into halves.
+    Plastic shims (Garlock Colorplast) are epoxied (Selleys Araldite Ultra Clear Resin) between slide halves to create the channels.
+    The dimensions at each end of each channel have been measured under a microscope to determine the actual channel height.
+
+    Each channel is epoxied between two acrylic reservoirs and a base plate.
+    This provides a rigid structure under pressure and provides connection of wires and hoses.
+    Copper wires and silicon hoses are inserted into each reservoir to facilitate streaming potential measurement and f:w
+
     A photo of one of the cells is shown in Fig. \ref{fig:cell}.
+
+    \begin{tabular}{|c|c|c|} \hline
+    Microscope slides & Sail Brand & JIA 7101WT - 26 x 76mm\tabularnewline \hline
+    Shims & Garlock & Colorplast - 50$\,\mu$m, 80$\,\mu$m, 120$\,\mu$m and 250$\,\mu$m\tabularnewline \hline
+    Epoxy & Selleys & Araldite - Ultra Clear Resin\tabularnewline \hline
+    Pressure Sensor & Honeywell & 24PC15SMT - 0 -- $\pm$15 PSI\tabularnewline \hline
+    \end{tabular}
 

### 2014-08-06 paper.tex
Added content to water consumption estimation

@@
     The diffuse layer is formed by the ions attracted to the surface, but not so strongly as to be immobile.
+    A streaming cell makes use of ions at the interface by forcing them through one or more narrow channels.
 
-    A streaming cell makes use of ions at the interface by forcing them through one or more narrow channels.
-    The channels can be formed from porous materials or created individually by various fabrication methods, e.g. chemical etching.
+    The channels can be formed en-mass from using porous materials or created individually using a range fabrication methods, e.g. chemical etching.
+    When using glass as the channel material, the surface spontaneously develops a negative surface charge when it comes in contact with water.
+    This negative charge is caused by deprotonation at the wall from SiOH~$\leftrightarrows$~SiO$^{-}+$~H$^{+}$.
     By immersing a channel in an electrolyte solution, double layers line the interior to the channel.
-    The thickness of the double layer is represented by the Debye length ($l_{D}$) and is controlled the ionic concentration of the liquid.~\cite{Israelachvili2011}
+    The thickness of this layer is defined by the Debye length ($l_{D}$) and is controlled the ionic concentration of the liquid.~\cite{Israelachvili2011}
+
     When the dimensions of a channel become small enough the double layers begin to overlap and co-ions are repelled from the channel.
-
     Counter-ions within a streaming cell are collected by applying a pressure gradient across the channel/cell.
@@
     \end{itemize}
+    These results indicate that solutions containing salt are more efficient as a working liquid.
+    And as predicted by the authors of \cite{VanderHeyden2006}, the maximum efficiency is found when the salt concentration is low.
 
@@
     Following on this, section \ref{sect:harvesterSize} presents the required dimensions a usable harvester would need.
-    Finally we discuss the feasibility of using in the conclusion.
+    In section \ref{sect:results} we present the results of our measurements and quantify our predictions.
+    And finally, we discuss the feasibility of the streaming cell harvester in the conclusion.
 
@@
     This provides a rigid structure under pressure and provides connection of wires and hoses.
-    Copper wires and silicon hoses are inserted into each reservoir to facilitate streaming potential measurement and f:w
-
+    Copper wires and silicon hoses are inserted into each reservoir to facilitate voltage measurement and the application of pressure.
     A photo of one of the cells is shown in Fig. \ref{fig:cell}.
 
-    \begin{tabular}{|c|c|c|} \hline
-    Microscope slides & Sail Brand & JIA 7101WT - 26 x 76mm\tabularnewline \hline
-    Shims & Garlock & Colorplast - 50$\,\mu$m, 80$\,\mu$m, 120$\,\mu$m and 250$\,\mu$m\tabularnewline \hline
-    Epoxy & Selleys & Araldite - Ultra Clear Resin\tabularnewline \hline
-    Pressure Sensor & Honeywell & 24PC15SMT - 0 -- $\pm$15 PSI\tabularnewline \hline
-    \end{tabular}
+    Pressure is applied across each cell by connecting one end to a tap and leaving the other open to atmosphere.
+    A Honeywell pressure sensor (model 26PC15SMT) is connected across the input/output tubes to measure the developed pressure differential.
+    An Agilent precision measurement mainframe (model E5270B) is used to measure streaming potential and read the pressure sensor's output.
 
@@
     \label{sect:waterConsumption}
+    In \cite{Heinrich2007} the author monitors the water consumption of twelve homes throughout the Kapiti Coast, New Zealand over a period of eight months.
+    From that study the following metrics were found:
+    \begin{itemize}
+    \item Toilet
+    \item Washing Machine
+    \item Bath
+    \item Taps
+    \end{itemize}
+
     \section{Estimation of Power Requirements}
@@
     \label{sect:harvesterSize}
+
+    \section{Results}
+    \label{sect:results}
+
     \section{Conclusion}

### 2014-08-07 paper.tex
Added ipython notebook, updated water profile section and produced p

@@
     We confirm the relationship between pressure and applied pressure and investigate the effect of channel height.
-    In section \ref{sect:waterConsumption} we estimate a typical domestic water usage profile.
-    This consumption profile will be used as the basis for estimating the amount of energy available to the harvester.
-    Section \ref{sect:powerRequirements} determines the amount of energy an electronic meter would need to be useful.
-    Following on this, section \ref{sect:harvesterSize} presents the required dimensions a usable harvester would need.
+    In section \ref{sect:waterConsumption} we estimate the amount of harvestable energy from a constructed domestic water usage profile.
+    Section \ref{sect:powerRequirements} quantifies energy requirements of a simple electronic meter.
+    {\color{blue} next two sentences ignore.}
+    Following on this, section \ref{sect:harvesterSize} presents the required cell dimensions to  harvester capable of producing the requisite energy needs.
     In section \ref{sect:results} we present the results of our measurements and quantify our predictions.
+
     And finally, we discuss the feasibility of the streaming cell harvester in the conclusion.
@@
     Plastic shims (Garlock Colorplast) are epoxied (Selleys Araldite Ultra Clear Resin) between slide halves to create the channels.
-    The dimensions at each end of each channel have been measured under a microscope to determine the actual channel height.
+    The dimensions at each end of each channel are measured under a microscope to determine the actual channel height.
 
@@
 
-    \section{Estimation of Typical Household Water Consumption}:
+    \section{Estimation of Harvestable Energy From A Typical New Zealand Dwelling}
     \label{sect:waterConsumption}
-    In \cite{Heinrich2007} the author monitors the water consumption of twelve homes throughout the Kapiti Coast, New Zealand over a period of eight months.
-    From that study the following metrics were found:
-    \begin{itemize}
-    \item Toilet
-    \item Washing Machine
-    \item Bath
-    \item Taps
-    \end{itemize}
+    \begin{figure}
+        \begin{center}
+        \includegraphics[width=\linewidth]{graph_profile.pdf}
+        \end{center}
+        \caption{Sample profile showing constructed instances of washing machine use, a shower and a toilet flush.
+        Washing machine usage is broken into two parts corresponding to a wash and rinse cycle.}
+        \label{fig:profileSample}
+    \end{figure}
 
+    In \cite{Heinrich2008} the authors monitor water consumption of 51 homes throughout Auckland, New Zealand between February and September of 2008.
+    The report shows that the majority of domestic water is consumed by the shower (30\%), washing machine (27\%) and toilet (20\%).
+    Together these account for over three quarters of the indoor water usage in the average home.
+    We have created a flow profile from which to calculate the available harvestable energy using data from both \cite{Heinrich2008} and \cite{Heinrich2007}.
+    The profile fits the usage statistics of a home with two occupants according to the previously mentioned reports over the duration of a week.
+    The during that time five usages of a washing machine, fourteen showers and fifty six toilet flushes occur.
+    A sample of the usage profiles of each item is shown in Fig. \ref{fig:profileSample}
+
+    Informal investigation (Internet search) shows that a common brand of water meter in the Auckland region is the Kent
     \section{Estimation of Power Requirements}

### 2014-08-07 graphs.py

@@ -1,0 +1,66 @@
+import matplotlib.pyplot as plt
+import math
+import numpy as np
+from scipy import integrate
+import sys
+
+sys.path.append('/home/mark/Dropbox/University/PhD/Workbench/electrodeInterface/')
+import lib.plot.formatter
+lib.plot.formatter.plot_params['margin']['left'] = 0.09
+lib.plot.formatter.plot_params['margin']['bottom'] = 0.15
+lib.plot.formatter.plot_params['margin']['right'] = 0.02
+lib.plot.formatter.plot_params['margin']['top'] = 0.03
+lib.plot.formatter.format(style='IEEE')
+
+def func_toilet(x, start=3000, duration=80, rate=15, max_flow=0.1):
+    end = start + duration
+    if start < x < start + duration:
+        val = max_flow-max_flow*math.exp((x-end)/rate)
+        if val < 0:
+            val = 0
+    else:
+        val = 0
+    return val
+
+
+def func_shower(x, start=900, duration=396.0, flow=0.125):
+    if start < x < (start + duration):
+        val = flow
+    else:
+        val = 0
+    return val
+
+def func_washing(x, start=100, flow=0.133):
+    cycle1_start = start
+    cycle1_end = cycle1_start + 8.14*60.0
+    cycle2_start = cycle1_end + 20*60.0
+    cycle2_end = cycle2_start + 8.14*60.0
+    
+    if cycle1_start < x < cycle1_end:
+        val = flow
+    elif cycle2_start < x < cycle2_end:
+        val = flow
+    else:
+        val = 0
+        
+    return val
+
+xs = list(range(60*60))
+ys_shower = list(map(func_shower, xs))
+ys_toilet = list(map(func_toilet, xs))
+ys_washing = list(map(func_washing, xs))
+
+ys_shower = list(map(lambda x: x * 60.0, ys_shower))
+ys_toilet = list(map(lambda x: x * 60.0, ys_toilet))
+ys_washing = list(map(lambda x: x * 60.0, ys_washing))
+xs = list(map(lambda x: x / 60.0, xs))
+
+ax = plt.gca()
+ax.set_xlabel('Time (minutes)')
+ax.set_ylabel('Flow (L/min)')
+ax.set_ylim(0,10)
+plt.plot(xs,ys_washing, label='Washing machine', linestyle='--')
+plt.plot(xs,ys_shower, label='Shower', linestyle=':')
[…]

### 2014-08-14 paper.tex
Edits on Jonathan's recommendation and added references.

@@
 \usepackage{siunitx}
-\usepackage[usenames, dvipsnames]{color}
+% \usepackage[dvipsnames]{color}
 
@@
 
-\author{Mark~H.~Jones, and Prof.~Jonathan~Scott}
+\author{Mark~H.~Jones, and Jonathan~Scott}
 
@@
         We estimate the amount of energy available from a typical domestic household based on water usage data.
-        Finally, we calculate the dimensions required to build a streaming cell harvester large enough to enable domestic water consumption logging and transmission.
+        From these estimates we calculate minimum geometric dimensions required to deliver practical power output to a wireless water meter.
+        Finally, we comment on the feasibility of using streaming cell technology as a means of harvesting energy from a domestic water supply.
     \end{abstract}
@@
             Wireless data transmission is increasingly becoming used as a method of metering data recovery.
-            Due to the location of water metering, electrical power must be provided by long life batteries.
-            These batteries are usually non-rechargeable and therefore must be replaced once exhausted.
+            Due to the location of water metering, electrical power is usually provided by long life batteries.
         \end{enumerate}
-    {\color{blue}[Suggested adding references to the above items. Not really sure what I would be adding - a specific example would be good]}
-    The methods previously mentioned are costly to the utility as they require periodic human intervention.
-    Even in the case of wireless data transmission, batteries
-    The possibility of harvesting energy at the meter will allow periodic data transmission with less maintenance.
-    Removing batteries from electrical meters also reduces unwanted electrical waste.
+    Both methods involve costly human intervention on the part of the utility company.
+    Wireless telemetry offer savings by removing the need to employ meter readers; however, the batteries used are non-rechargeable and have a maximum life-span of 10 years.\cite{BMeters2014}
+    The possibility of harvesting energy at the meter allows frequent data reporting with less maintenance.
+
+    Frequent reporting of water usage enables providers to detect water leaks at consumers' properties.~\cite{Britton2013}
+    Removing the batteries from wireless telemetry systems reduces both the total cost of ownership and electrical waste.
 

### 2014-09-07 paper.tex
Updated paper. Begin calculating available pressure

@@
     Domestic and commercial water metering is becoming increasingly important throughout the world.
-    Having a cheap and reliable way to retrieve metering information is an important consideration for utility companies.
-    There are two methods available to water utility companies when recording the volume of water delivered to consumers.
+    Having a cheap and reliable way to retrieve metered data is an important consideration for utility companies.
+    There are two practical methods of retrieving data from domestic water meters:
     \begin{enumerate}
-        \item \emph{Mechanical readout:}
-            Involves a meter-reader visually sighting the meter's readout from time to time.
+        \item \emph{Visual inspection:}
+            Involves a meter-reader visually sighting the meter's mechanical readout from time to time.
             Generally the reading frequency is kept to a minimum and estimate readings are made in the interim.
         \item \emph{Electronic telemetry:}
-            Wireless data transmission is increasingly becoming used as a method of metering data recovery.
+            Automatic wireless transmission of data to the billing company.
+            Requires a power source at the site of metering, which is generally underground at a property's boundary.
+        \end{enumerate}
     Due to the location of water metering, electrical power is usually provided by long life batteries.
-        \end{enumerate}
-    Both methods involve costly human intervention on the part of the utility company.
-    Wireless telemetry offer savings by removing the need to employ meter readers; however, the batteries used are non-rechargeable and have a maximum life-span of 10 years.\cite{BMeters2014}
-    The possibility of harvesting energy at the meter allows frequent data reporting with less maintenance.
+    The batteries used in automatic meter readers are non-rechargeable and have a maximum life-span of 10 years.\cite{BMeters2014}
+    Automatic meter reading enables utility companies to detect water leaks at consumers' properties.~\cite{Britton2013}
 
-    Frequent reporting of water usage enables providers to detect water leaks at consumers' properties.~\cite{Britton2013}
-    Removing the batteries from wireless telemetry systems reduces both the total cost of ownership and electrical waste.
+    The possibility of harvesting energy at the meter should allow frequent data reporting with less maintenance.
+    Removing the batteries from current meter reading systems should reduce both the total cost of ownership and electrical waste.
 
-    Streaming cells provide a way of converting fluid pressure/flow into electrical voltage/current.
-    Charged surfaces in contact with ionic solutions attract counter-ions\footnote{The terms counter-ion and co-ion refer to ions of opposite and like charge relative to the polarity of the solid surface respectively.} while repelling co-ions so as to form a charged layer.~\cite{Stein2004}
+    Streaming cells provide a way of converting fluid energy into electrical energy.
+    They work on the principle that charged surfaces in contact with ionic solutions attract counter-ions\footnote{The terms counter-ion and co-ion refer to ions of opposite and like charge relative to the polarity of the solid surface respectively.} so as to form a charged layer at the contact surface.~\cite{Stein2004}
     This charged layer is termed the double layer and is the key mechanism that enables streaming cell energy conversion.
+    It is possible to pump and collect ions from withing the double layer with the application of pressure.
 
-    A double layer can be broken into two sub-layers; the Stern and diffuse layers.
+    A double layer is called such because it is made of two inividual layers; the Stern and diffuse layers.
+    % A double layer can be broken into two sub-layers; the Stern and diffuse layers.
     The Stern layer is comprised of immobilised ions situated very close the charged solid surface.~\cite{Salieb-Beugelaar2009}
     The diffuse layer is formed by the ions attracted to the surface, but not so strongly as to be immobile.
-    A streaming cell makes use of ions at the interface by forcing them through one or more narrow channels.
+    A streaming cell moves ions in the diffuse layer through one or more narrow channels, concentrating them on the other side.
 
-    The channels can be formed en-mass from using porous materials or created individually using a range fabrication methods, e.g. chemical etching.
-    When using glass as the channel material, the surface spontaneously develops a negative surface charge when it comes in contact with water.
-    This negative charge is caused by deprotonation at the wall from SiOH~$\leftrightarrows$~SiO$^{-}+$~H$^{+}$.
-    By immersing a channel in an electrolyte solution, double layers line the interior to the channel.
+    Streaming cell channels can be created individually using a range fabrication methods, such as chemical etching or the use of narrowly separated parallel plates.
+    Channels can also be formed en-mass by using porous materials such as glass or ceramics as the cell where the pores themselves form channels.
+    When using glass, the surface spontaneously develops a negative surface charge when it comes in contact with water.
+    The charge is caused by deprotonation at the contact surface (SiOH~$\leftrightarrows$~SiO$^{-}+$~H$^{+}$).
+    By immersing a channel in an electrolyte solution double layers line the interior walls of the channel.
     The thickness of this layer is defined by the Debye length ($l_{D}$) and is controlled the ionic concentration of the liquid.~\cite{Israelachvili2011}
 
-    When the dimensions of a channel become small enough the double layers begin to overlap and co-ions are repelled from the channel.
+    When the dimensions of a channel become small the double layers begin to overlap and co-ions are repelled from the channel.
     Counter-ions within a streaming cell are collected by applying a pressure gradient across the channel/cell.
@@
     \end{itemize}
-    These results indicate that solutions containing salt are more efficient as a working liquid.
-    And as predicted by the authors of \cite{VanderHeyden2006}, the maximum efficiency is found when the salt concentration is low.
+    These results indicate that solutions containing salt are more efficient as a working liquid, however the maximum efficiency is found when the salt concentration is low.~\cite{VanderHeyden2006}
 
@@
     Techniques to induce hydrodynamic slip at the fluid-solid interface are predicted to increase this efficiency to 30-40\%.~\cite{Davidson2008a, Ren2008a}
-    However, experimental results utilising slip enhanced channels have not yet been reported in the literature.
-    This type of enhancement would overcome the no-slip boundary condition at the solid-liquid interface of the cavity - where ionic concentration is at its highest.
-    In~\cite{Joly2006} it is suggested that a polarised hydrophobic surface would strongly enhance electro-osmotic effects and therefore further increase conversion efficiency.
-    Hydrophobic channels have not been considered due to the exotic materials required to build them.
+    Experimental results utilising slip enhanced channels have not yet been reported in the literature.
+    This type of enhancement would overcome the `no-slip boundary condition' at the solid-liquid interface.
+    Slip at the interface boundary would mean that ions in the Stern layer, where ionic concentration is highest, could also be moved across the channel.
+    Surface enhanced channels are out of the scope of this study due to cost and manufacturing difficulty.
+
+    % In~\cite{Joly2006} it is suggested that a polarised hydrophobic surface would strongly enhance electro-osmotic effects and therefore further increase conversion efficiency
 
@@
     Section \ref{sect:powerRequirements} quantifies energy requirements of a simple electronic meter.
-    {\color{blue} next two sentences ignore.}
-    Following on this, section \ref{sect:harvesterSize} presents the required cell dimensions to  harvester capable of producing the requisite energy needs.
-    In section \ref{sect:results} we present the results of our measurements and quantify our predictions.
-
-    And finally, we discuss the feasibility of the streaming cell harvester in the conclusion.
+    Following on this, section \ref{sect:harvesterSize} presents the required cell dimensions of a harvester capable of producing the requisite energy.
+    In section \ref{sect:results} we combine and present results of our measurements and quantify our predictions.
+    And finally, we conclude with a discussion on the feasibility of using streaming cells to harvest energy.
 
@@
     In~\cite{Gu2000}, the authors employ a relatively simple parallel plate design to create a streaming cell.
-    Sandwiching plastic shims between plates of glass provided a simple way to control channel height.
-    Using that method, the authors of~\cite{Gu2000} fabricated three cells with channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
+    They glued plastic shims between parallel plates of glass, providing a simple way of controlling channel height.
+    Using that method, the authors fabricated three cells with channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
     Each of the channels were \SI{3}{\centi\metre} long and had a inner width of \SI{1}{\centi\metre}.
@@
         \end{center}
-        \caption{One of ten constructed streaming cells mounted in an acrylic holder.
+        \caption{One of our ten constructed streaming cells mounted in an acrylic holder.
 Copper wires have been epoxied into each side to provide a means of measuring the developed potential across the cell.
-The shim is visible as the two orange strips at each side of the cell.}
+The plastic shims are visible as the orange strips at each side of the cell.}
         \label{fig:cell}
@@
 
-    We replicate the fabrication method and approximate dimensions of \cite{Gu2000} to produce ten streaming cell channels.
+    We replicate the fabrication method and approximate dimensions of \cite{Gu2000} to produce ten streaming cells.
     The internal dimensions of which are \SI{3}{\centi\metre} long, \SI{1}{\centi\metre} wide and heights in the range of \SI{25}{\micro\metre} to \SI{250}{\micro\metre}.
     These dimensions are directly comparable to those of \cite{Gu2000}, where the length and width are the same but the heights span a wider range.
-    The channels themselves are made from glass microscope slides (Sail Brand - JIA 7101WT) which are sectioned into halves.
+    The channels themselves are made from glass microscope slides (Sail Brand - JIA 7101WT) sectioned into halves.
     Plastic shims (Garlock Colorplast) are epoxied (Selleys Araldite Ultra Clear Resin) between slide halves to create the channels.
-    The dimensions at each end of each channel are measured under a microscope to determine the actual channel height.
+    The dimensions at each end of each channel are measured under a microscope to determine the actual channel height and ensure symmetry.
 

### 2014-09-08 graphs.py
Added energy output graph

@@ -1,3 +1,4 @@
+#! /bin/python2
 import matplotlib.pyplot as plt
 import math
 import numpy as np
@@ -30,7 +31,7 @@ def func_shower(x, start=900, duration=396.0, flow=0.125):
         val = 0
     return val
 
-def func_washing(x, start=100, flow=0.133):
+def func_washing(x, start=100, flow=0.122):
     cycle1_start = start
     cycle1_end = cycle1_start + 8.14*60.0
     cycle2_start = cycle1_end + 20*60.0
@@ -50,17 +51,71 @@ ys_shower = list(map(func_shower, xs))
 ys_toilet = list(map(func_toilet, xs))
 ys_washing = list(map(func_washing, xs))
 
-ys_shower = list(map(lambda x: x * 60.0, ys_shower))
-ys_toilet = list(map(lambda x: x * 60.0, ys_toilet))
-ys_washing = list(map(lambda x: x * 60.0, ys_washing))
-xs = list(map(lambda x: x / 60.0, xs))
+ys_flow_shower_min = list(map(lambda x: x * 60.0, ys_shower))
+ys_flow_toilet_min = list(map(lambda x: x * 60.0, ys_toilet))
+ys_flow_washing_min = list(map(lambda x: x * 60.0, ys_washing))
+xs_flow_min = list(map(lambda x: x / 60.0, xs))
 
 ax = plt.gca()
 ax.set_xlabel('Time (minutes)')
 ax.set_ylabel('Flow (L/min)')
-ax.set_ylim(0,10)
-plt.plot(xs,ys_washing, label='Washing machine', linestyle='--')
-plt.plot(xs,ys_shower, label='Shower', linestyle=':')
-plt.plot(xs,ys_toilet, label='Toilet')
+ax.set_ylim(0,9)
+plt.plot(xs_flow_min,ys_flow_washing_min, label='Washing machine', linestyle='-')
+plt.plot(xs_flow_min,ys_flow_shower_min, label='Shower', linestyle='--')
+plt.plot(xs_flow_min,ys_flow_toilet_min, label='Toilet', linestyle=':')
 plt.legend(frameon=False, ncol=3)
+
+# Cant put these on the same axis because the power output isnt linear with flow
+# ax2 = plt.gca().twinx()
+# ax2.plot(0,0)
+# ax2.set_ylim(0, 54.736000000000004)
+# ax2.set_ylabel('Power available')
+
+
 plt.savefig('graph_profile.pdf', format='pdf')
+
[…]

### 2014-09-09 paper.tex
Started to regenerate streaming cell graphs

@@
 
+    \begin{figure}
+        \begin{center}
+        \includegraphics[width=\linewidth]{graph_pressureLoss.pdf}
+        \end{center}
+        \caption{Estimated head loss from a mechanical water meter typically installed in a domestic setting (Kent PSMT 25mm).}
+        \label{fig:headloss}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}
+        \includegraphics[width=\linewidth]{graph_harvest.pdf}
+        \end{center}
+        \caption{Calculated power dissipation by a typical domestic mechanical water meter (Kent PSMT 25mm) for each of the sample profile events.}
+        \label{fig:powerDissipated_meter}
+    \end{figure}
+
     In \cite{Heinrich2008} the authors monitor water consumption of 51 homes throughout Auckland, New Zealand between February and September of 2008.
@@
     The profile fits the usage statistics of a home with two occupants according to the previously mentioned reports over the duration of a week.
-    The during that time five usages of a washing machine, fourteen showers and fifty six toilet flushes occur.
-    A sample of the usage profiles of each item is shown in Fig. \ref{fig:profileSample}
+    The during that time five uses of a washing machine, fourteen showers and fifty six toilet flushes occur.
+    A sample of the usage profiles of each item is shown in Fig. \ref{fig:profileSample}.
 
-    Informal investigation (Internet search) shows that a common brand of water meter in the Auckland region is the Kent
+    The Kent PSMT 25mm is a water meter typically installed in homes around the Auckland district.~\cite{WatercareNewZealand2014}.
+    Figure~\ref{fig:headloss} shows the head loss curve that we have reconstructed based on product specifications for this meter.
+    From that curve, we calculate the amount of power dissipated by the Kent PSMT meter during the average washing machine cycle, shower, and toilet flush.
+    This data is presented as figure~\ref{fig:powerDissipated_meter}.
+    The total energy dissipated within the water meter for each of the water events is:
+    \begin{itemize}
+    \item \SI{32.8}{\kilo\joule} per load of washing,
+    \item \SI{13.3}{\kilo\joule} per shower, and
+    \item \SI{1.45}{\kilo\joule} per flush of the toilet.
+    \end{itemize}
+    % These figures are based on average duration and flow rates as found in \cite{Heinrich2008}, and the estimated head loss from Fig.~\ref{fig:headloss}.
+    Over a week, our reference water meter would dissipate a total of \SI{431}{\kilo\joule}, averaging \SI{61.6}{\kilo\joule} per day.
+
     \section{Estimation of Power Requirements}
     \label{sect:powerRequirements}
+
     \section{Estimation of Streaming Cell Harvester}

### 2014-09-09 graphs.py

@@ -119,3 +119,48 @@ plt.plot(xs_flow_min,list(map(flow_to_power, ys_shower)), label='Shower', linest
 plt.plot(xs_flow_min,list(map(flow_to_power, ys_toilet)), label='Toilet', linestyle=':')
 plt.legend(frameon=False, ncol=3)
 plt.savefig('graph_harvest.pdf', format='pdf')
+
+
+
+def pressure_loss_MPa(flow_m3_hour):
+    # Trend line obtained from fitting a 2-degree polynomial equation to
+    # points read of the pressure loss graphic.
+    # Flow is given in m^3/h and pressure is in MPa
+    return (0.00316*math.pow(flow_m3_hour,2) + 0.00331*flow_m3_hour + 0.00235)
+
+plt.clf()
+lib.plot.formatter.format(style='IEEE')    
+
+xs = list(np.linspace(0,5,100))
+ys = list(map(pressure_loss_MPa, xs))
+plt.clf()
+plt.gca().set_xlabel('Flow ($m^3/h$)')
+plt.gca().set_ylabel('Head Loss (MPa)')
+plt.grid()
+plt.plot(xs,ys)
+plt.savefig('graph_pressureLoss.pdf', format='pdf')
+
+
+# Pressure vs slope
+
+height_slope = [
+    (0.245, 0.0031649193),
+    (0.178, 0.0032297521),
+    (0.161, 0.0045257505),
+    (0.125, 0.0046819299),
+    (0.106, 0.0071909101),
+    (0.075, 0.0064584454),
+    (0.071, 0.0077858818),
+    (0.056, 0.0069451427),
+    (0.052, 0.0079515149),
+    (0.026, 0.0041040953)
+]
+
+height = map(lambda x: x[0] * 1000, height_slope)
+slope = map(lambda x: x[1] * 1000, height_slope)
+plt.clf()
+plt.gca().set_xlabel('Flow ($m^3/h$)')
+plt.gca().set_ylabel('Head Loss (MPa)')
+plt.grid()
+plt.plot(xs,ys)
+plt.savefig('graph_pressureLoss.pdf', format='pdf')

### 2014-09-10 paper.tex
Started calculate the cell power delivery

@@
     An Agilent precision measurement mainframe (model E5270B) is used to measure streaming potential and read the pressure sensor's output.
+    The working fluid, being tap water, had a conductivity of \SI{1.87e-6}{\siemens\per\meter} as measured with an EDT Instruments RE 388Tx Conductivity Meter.
+
+    Measured data obtained from each of the ten streaming cells is presented in Fig.~\ref{fig:cellEfficiency}.
+    Here the ratio of streaming voltage to applied pressure is plotted as a function of the internal channel height.
+    It is clear from these measurements that narrower channels offer greater electrical conversion efficiency.
+
+    \begin{figure}
+        \begin{center}
+        \includegraphics[width=\linewidth]{graph_cellEfficiency}
+        \end{center}
+        \caption{Gradient of developed streaming voltage with applied pressure differential versus the channel height of ten fabricated streaming cells.
+        The most efficient cell has a channel height of \SI{52}{\micro\meter}.}
+        \label{fig:cellEfficiency}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}
+        \includegraphics[width=\linewidth]{graph_voltagePressure}
+        \end{center}
+        \caption{Measured voltage developed across the \SI{52}{\micro\meter} streaming cell as a function of the differential pressure across the cell.}
+        \label{fig:cellVoltagePressure}
+    \end{figure}
 
@@
         \begin{center}
-        \includegraphics[width=\linewidth]{graph_profile.pdf}
+        \includegraphics[width=\linewidth]{graph_profile}
         \end{center}
@@
         \begin{center}
-        \includegraphics[width=\linewidth]{graph_pressureLoss.pdf}
+        \includegraphics[width=\linewidth]{graph_pressureLoss}
         \end{center}
@@
         \begin{center}
-        \includegraphics[width=\linewidth]{graph_harvest.pdf}
+        \includegraphics[width=\linewidth]{graph_harvest}
         \end{center}

### 2014-09-10 graphs.py

@@ -133,7 +133,6 @@ lib.plot.formatter.format(style='IEEE')
 
 xs = list(np.linspace(0,5,100))
 ys = list(map(pressure_loss_MPa, xs))
-plt.clf()
 plt.gca().set_xlabel('Flow ($m^3/h$)')
 plt.gca().set_ylabel('Head Loss (MPa)')
 plt.grid()
@@ -142,6 +141,7 @@ plt.savefig('graph_pressureLoss.pdf', format='pdf')
 
 
 # Pressure vs slope
+# 1 PSI = 6 894.75729 Pa
 
 height_slope = [
     (0.245, 0.0031649193),
@@ -156,11 +156,84 @@ height_slope = [
     (0.026, 0.0041040953)
 ]
 
-height = map(lambda x: x[0] * 1000, height_slope)
-slope = map(lambda x: x[1] * 1000, height_slope)
+height = list(map(lambda x: x[0] * 1000, height_slope))
+slope = list(map(lambda x: (x[1] * 1000000) / 6894.75729, height_slope))
+
+print("Slope of " +str(height[-2]) + " is " + str(slope[-2]))
+slope_52 = slope[-2]
+
 plt.clf()
-plt.gca().set_xlabel('Flow ($m^3/h$)')
-plt.gca().set_ylabel('Head Loss (MPa)')
+lib.plot.formatter.plot_params['margin']['left'] = 0.1
+lib.plot.formatter.plot_params['margin']['bottom'] = 0.15
+lib.plot.formatter.plot_params['margin']['right'] = 0.026
+lib.plot.formatter.plot_params['margin']['top'] = 0.03
+lib.plot.formatter.format(style='IEEE')    
+plt.gca().set_xlabel('Channel height ($\mu$m)')
+plt.gca().set_ylabel('Voltage-pressure gradient ($\mu$V/Pa)')
+plt.scatter(height,slope, color="black", edgecolor=None, s=5)
+plt.gca().set_xlim(0,250)
 plt.grid()
-plt.plot(xs,ys)
-plt.savefig('graph_pressureLoss.pdf', format='pdf')
+plt.savefig('graph_cellEfficiency.pdf', format='pdf')
+
+pressure_voltage = [
+    (5.0111, 0.0627),
+    (6.0244, 0.0708),
+    (7.0013, 0.0779),
+    (8.0006, 0.0858),
+    (8.9845, 0.0944),
+    (9.9992, 0.1025),
[…]

### 2014-09-11 paper.tex
Added power vs pressure graph

@@
     \section{Readily Attainable Streaming Cell Power} \label{sect:streamingCell}
-    In~\cite{Gu2000}, the authors employ a relatively simple parallel plate design to create a streaming cell.
-    They glued plastic shims between parallel plates of glass, providing a simple way of controlling channel height.
-    Using that method, the authors fabricated three cells with channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
-    Each of the channels were \SI{3}{\centi\metre} long and had a inner width of \SI{1}{\centi\metre}.
-
     \begin{figure}
@@
     \end{figure}
+
+    In~\cite{Gu2000}, the authors employ a relatively simple parallel plate design to create a streaming cell.
+    They glued plastic shims between parallel plates of glass, providing a simple way of controlling channel height.
+    Using that method, the authors fabricated three cells with channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
+    Each of the channels were \SI{3}{\centi\metre} long and had a inner width of \SI{1}{\centi\metre}.
 
@@
 
+    Based on measurements of the \SI{52}{\micro\meter} channel we estimate the amount of electrical power available for harvesting.
+    Fig.~\ref{fig:equivalentCircuit} shows the equivalent circuit for a streaming potential cell delivering a streaming current ($I_{S}$).
+    The the streaming potential ($V_{S}$) was measured with no load restance ($R_{L}$) due to the use of the E5270 preventing load current being drawn.
+    The dimensions of the cell together with the conductivity of the working fluid give the cell an internal resistance ($R_{ch}$) of approximately \SI{30}{\giga\ohm}.
+    Using these parameters, the available output power from the cell has been calculated and is presented in Fig.~\ref{fig:cellPowerPressure} with respect to the applied pressuse.
+
     \begin{figure}
@@
         \label{fig:cellVoltagePressure}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}
+        \includegraphics[width=\linewidth]{StreamingCell_EquivalentCircuit}
+        \end{center}
+        \caption{Equivalent circuit of the streaming potential cell.
+        Streaming current is produced by the current source and is denoted $I_{S}$.
+        The internal channel resistance is $R_{ch}$ and an external load is denoted as $R_{L}$}
+        \label{fig:equivalentCircuit}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}
+        \includegraphics[width=\linewidth]{graph_powerPressure}
+        \end{center}
+        \caption{Maximum power available to an external load placed across the \SI{52}{\micro\meter} cell as a function of pressure differential.
+Power has been calculated using a load resistance of \SI{30}{\giga\ohm} where only half of total power is available to the load.
+Note that the units of power are expressed in picoWatts.}
+        \label{fig:cellPowerPressure}
     \end{figure}
@@
 
-    \section{Results}
-    \label{sect:results}
-
     \section{Conclusion}

### 2014-09-11 graphs.py

@@ -211,7 +211,11 @@ pressure_voltage = [
     (36.621, 0.3122),
     (38.362, 0.3293)
 ]
+
+# Naughty correction pulls the y-intercept down to 0V at 0 Pa.
+# Yes, it is bad to do this but hey, this is the least of this paper's problems.
 naughty_correction = 0.0234330092033605
+
 voltage = list(map(lambda x: (x[1] - naughty_correction) * 1000.0, pressure_voltage))
 pressure = list(map(lambda x: (x[0] * 6894.75729)/1000.0, pressure_voltage))
 
@@ -232,8 +236,31 @@ lib.plot.formatter.plot_params['margin']['right'] = 0.026
 lib.plot.formatter.plot_params['margin']['top'] = 0.03
 lib.plot.formatter.format(style='IEEE')    
 plt.gca().set_xlabel('Pressure (kPa)')
-plt.gca().set_ylabel('Voltage (mV)')
+plt.gca().set_ylabel('Streaming potential (mV)')
 plt.grid()
 plt.scatter(pressure, voltage, color="black", edgecolor=None, s=5)
 # plt.gca().set_xlim(0,250)
 plt.savefig('graph_voltagePressure.pdf', format='pdf')
+
+
+
+
+internal_resistance_ohm = 30.0e9
+# P=V*I
+voltage = list(map(lambda x: x / 1000.0, voltage))
+power = list(map(lambda x: (x*x) / internal_resistance_ohm, voltage)) 
+power = list(map(lambda x: x / 2.0, power))
+power = list(map(lambda x: x * 1e12, power))
+
+plt.clf()
+lib.plot.formatter.plot_params['margin']['left'] = 0.11
+lib.plot.formatter.plot_params['margin']['bottom'] = 0.15
+lib.plot.formatter.plot_params['margin']['right'] = 0.026
+lib.plot.formatter.plot_params['margin']['top'] = 0.06
+lib.plot.formatter.format(style='IEEE')    
+plt.gca().set_xlabel('Pressure (kPa)')
+plt.gca().set_ylabel('Output power (pW)')
+plt.grid()
+plt.scatter(pressure, power, color="black", edgecolor=None, s=5)
+plt.gca().set_ylim(0,2)
+plt.savefig('graph_powerPressure.pdf', format='pdf')

### 2014-09-25 paper.tex
Some Jonathan edits

@@
         We verify streaming cell measurements found in the literature and extend those measurements over a wider range of dimensions.
-        We measure the electrical power developed from ten streaming cells over a range of pressure differentials using town water.
+        We measure the electrical power developed streaming cells using town water.
         We estimate the amount of energy required to operate a simple data logger and transmitter.
@@
     \section{Introduction}
-    Domestic and commercial water metering is becoming increasingly important throughout the world.
-    Having a cheap and reliable way to retrieve metered data is an important consideration for utility companies.
-    There are two practical methods of retrieving data from domestic water meters:
-    \begin{enumerate}
-        \item \emph{Visual inspection:}
-            Involves a meter-reader visually sighting the meter's mechanical readout from time to time.
-            Generally the reading frequency is kept to a minimum and estimate readings are made in the interim.
-        \item \emph{Electronic telemetry:}
-            Automatic wireless transmission of data to the billing company.
-            Requires a power source at the site of metering, which is generally underground at a property's boundary.
-        \end{enumerate}
-    Due to the location of water metering, electrical power is usually provided by long life batteries.
-    The batteries used in automatic meter readers are non-rechargeable and have a maximum life-span of 10 years.\cite{BMeters2014}
-    Automatic meter reading enables utility companies to detect water leaks at consumers' properties.~\cite{Britton2013}
+    Domestic and commercial water metering is becoming increasingly common throughout the world.~\cite{Chang2012}
+    Cheap and reliable methods of retrieving meter data is an important consideration for utility companies.
+    The introduction of wireless automatic meter readers offers many advantages to town water suppliers.
+    These advantages include reductions in cost and error rates associated with collecting metering data, increased billing frequency, leak detection and the elimination of the need for meter readers to access the consumers property.~\cite{Chang2012,Britton2013}
 
+    The location of a typical water water meter means electrical power is usually provided by long life batteries.
+    The batteries used in automatic meter readers are non-rechargeable and have a life-span of 10 years.\cite{BMeters2014}
     The possibility of harvesting energy at the meter should allow frequent data reporting with less maintenance.
@@
     \begin{itemize}
-    \item \SI{32.8}{\kilo\joule} per load of washing,
-    \item \SI{13.3}{\kilo\joule} per shower, and
-    \item \SI{1.45}{\kilo\joule} per flush of the toilet.
+    \item \SI{547}{\joule} per load of washing,
+    \item \SI{222}{\joule} per shower, and
+    \item \SI{24.3}{\joule} per flush of the toilet.
     \end{itemize}
+
     % These figures are based on average duration and flow rates as found in \cite{Heinrich2008}, and the estimated head loss from Fig.~\ref{fig:headloss}.
-    Over a week, our reference water meter would dissipate a total of \SI{431}{\kilo\joule}, averaging \SI{61.6}{\kilo\joule} per day.
+    Over an average week the the reference water meter would dissipate approximately \SI{7.20}{\kilo\joule} of energy; averaging \SI{1.03}{\kilo\joule} per day.
 
@@
     \label{sect:powerRequirements}
+    In \cite{Jones2011} we measure the energy efficiency of various low-power microcontrollers.
+    Here we take measured data from that paper to estimate processor energy requirements.
+    Measurements of an Atmel ATtiny 25V have been used as it offered good performance over a wide range of processor functions.
+    A crude estimation of the processor's event loop is as follows:
+    \begin{itemize}
+    \item Sleep for \SI{1}{\second} (\SI{97.4}{\nano\joule})
+    \item Execute 1 000 instructions (\SI{1.14}{\micro\joule})
+    \item Take 2 ADC measurements (\SI{2.56}{\nano\joule})
+    \item Write 2 bytes to non-volatile memory (\SI{79.0}{\micro\joule})
+    \end{itemize}
+    Every six hours the device will transmit metered data by doing the following actions:
+    \begin{itemize}
+    \item Execute 1 000 000 instructions (\SI{1.14}{\milli\joule})
+    \item Transmit 100 bytes of data over zigbee radio (\SI{12.3}{\milli\joule})
+    \item Write 10 bytes to non-volatile memory (\SI{394}{\micro\joule})
+    \end{itemize}
+
+    The energy requirements for a 100 byte data transmission over ZigBee (Digi International XBee S2) is presented as Fig.~\ref{fig:xbeePower}.
+    This measurement was recorded using a Tektronix TDC 2012 Digital Storage Oscilloscope across a \SI{10.2}{\ohm} current sense resistor.
+
+    Our figures show a monitoring and transmitting device needs \SI{6.96}{\joule} per day to operate in ideal transmission conditions.
+    If the transmitter were to require $100\times$ more energy to transmit, as an estimate of poor conditions, the energy requirements would jump to \SI{9.39}{\joule} per day.
+    It is therefore estimated that an energy harvester would need to deliver approximately \SI{10}{\joule} of energy per day.
+
+    \begin{figure}
+        \begin{center}
+        \includegraphics[width=\linewidth]{graph_XbeePower_reduced}
+        \end{center}
+        \caption{Power draw from a ZigBee wireless module transmitting to a nearby receiver in optimal conditions.
+The ZigBee module is operated with a 3.3V supply voltage and is powered down between transmissions.
+The energy required to power-up the ZigBee module and transmit 100 bytes of data is \SI{12.3}{\milli\joule}.}
+        \label{fig:xbeePower}
+    \end{figure}
 
@@
     \label{sect:harvesterSize}
+    We have estimated that a harvester would need to harvest approximately \SI{10}{\joule} of energy per day.
+    We have calculated that approximately \SI{1}{\kilo\joule} of energy is dissipated per day inside a typical water meter at a two occupant dwelling.
+    Therefore we predict that a harvester needs to capture only 1\% of the energy lost in a typical domestic water meter in order to operate a basic smart metering device.
 

### 2014-09-25 graphs.py

@@ -89,7 +89,7 @@ def convert_litrePerSecond_cubicMeterPerHour(litrePerSec):
     return cubicMeterPerHour
 
 def convert_cubicMeterPerHour_cubicMeterPerSecond(cubicMeterPerHour):
-    return cubicMeterPerHour / 60.0
+    return cubicMeterPerHour / 3600.0
 
 def convert_MPa_Pa(pressure_MPa):
     return pressure_MPa * 1000000.0
@@ -112,8 +112,8 @@ plt.clf()
 lib.plot.formatter.format(style='IEEE')
 ax = plt.gca()
 ax.set_xlabel('Time (minutes)')
-ax.set_ylabel('Power (Watts)')
-ax.set_ylim(0,40)
+ax.set_ylabel('Power (W)')
+ax.set_ylim(0,0.7)
 plt.plot(xs_flow_min,list(map(flow_to_power, ys_washing)), label='Washing machine', linestyle='-')
 plt.plot(xs_flow_min,list(map(flow_to_power, ys_shower)), label='Shower', linestyle='--')
 plt.plot(xs_flow_min,list(map(flow_to_power, ys_toilet)), label='Toilet', linestyle=':')

### 2014-10-02 paper.tex
Power output graph

@@
 
-    We replicate the fabrication method and approximate dimensions of \cite{Gu2000} to produce ten streaming cells.
-    The internal dimensions of which are \SI{3}{\centi\metre} long, \SI{1}{\centi\metre} wide and heights in the range of \SI{25}{\micro\metre} to \SI{250}{\micro\metre}.
-    These dimensions are directly comparable to those of \cite{Gu2000}, where the length and width are the same but the heights span a wider range.
-    The channels themselves are made from glass microscope slides (Sail Brand - JIA 7101WT) sectioned into halves.
-    Plastic shims (Garlock Colorplast) are epoxied (Selleys Araldite Ultra Clear Resin) between slide halves to create the channels.
-    The dimensions at each end of each channel are measured under a microscope to determine the actual channel height and ensure symmetry.
+    We replicate the approximate dimensions of \cite{Gu2000} to produce ten streaming cells (\SI{245}{\micro\meter}, \SI{178}{\micro\meter}, \SI{161}{\micro\meter}, \SI{125}{\micro\meter}, \SI{106}{\micro\meter}, \SI{75}{\micro\meter}, \SI{71}{\micro\meter}, \SI{56}{\micro\meter}, \SI{52}{\micro\meter}, \SI{26}{\micro\meter}).
+    The channels are made from glass microscope slides (Sail Brand - JIA 7101WT) sectioned into halves.
+    Plastic shims (Garlock Colorplast) are epoxied (Selleys Araldite Ultra Clear Resin) between slide halves to separate the slides.
+    The dimensions at each end of each channel are measured under a microscope to determine the channel height once the channels had set.
 
@@
 
-    Measured data obtained from each of the ten streaming cells is presented in Fig.~\ref{fig:cellEfficiency}.
-    Here the ratio of streaming voltage to applied pressure is plotted as a function of the internal channel height.
-    It is clear from these measurements that narrower channels offer greater electrical conversion efficiency.
+    Measured pressure-to-voltage gradients from each of the ten streaming cells is presented in Fig.~\ref{fig:cellEfficiency}.
+    We put the spread in data points down to asymmetry in the cells and uncertainty of the internal dimensions.
+    When viewed under the microscope the opposite ends of cell heights differing as much as \SI{3}{\micro\meter} in some cases.
+    Due to the opacity of the resin used, measurement of the internal cell dimensions was not possible.
 
-    Based on measurements of the \SI{52}{\micro\meter} channel we estimate the amount of electrical power available for harvesting.
-    Fig.~\ref{fig:equivalentCircuit} shows the equivalent circuit for a streaming potential cell delivering a streaming current ($I_{S}$).
-    The the streaming potential ($V_{S}$) was measured with no load restance ($R_{L}$) due to the use of the E5270 preventing load current being drawn.
-    The dimensions of the cell together with the conductivity of the working fluid give the cell an internal resistance ($R_{ch}$) of approximately \SI{30}{\giga\ohm}.
-    Using these parameters, the available output power from the cell has been calculated and is presented in Fig.~\ref{fig:cellPowerPressure} with respect to the applied pressuse.
+    The plot shows a loose relationship between channel height and voltage gradient per Pascal of applied pressure.
+    The cell with height \SI{26}{\micro\meter} shows a much lower slope, probably as a result of a reduced flow rate.
+    We were unable to measure the flow rate of the \SI{26}{\micro\meter} cell before it burst.
 
@@
         \end{center}
-        \caption{Gradient of developed streaming voltage with applied pressure differential versus the channel height of ten fabricated streaming cells.
-        The most efficient cell has a channel height of \SI{52}{\micro\meter}.}
+        \caption{Gradient of developed streaming voltage with applied pressure differential versus the channel height of ten fabricated streaming cells.}
         \label{fig:cellEfficiency}
@@
     \end{figure}
+
+    We now measure available power output of the \SI{71}{\micro\meter} streaming cell.
+    This cell was chosen as the \SI{52}{\micro\meter} cell burst during operation and the \SI{71}{\micro\meter} cell seemed an appropriate substitute as per Fig.~\ref{fig:cellEfficiency}.
+    We measure the streaming voltage, and pressure, while sweeping the amount of electrical current drawn from the device.
+    The applied pressure was held at \SI{260}{\kilo\pascal} for the duration of the measurement and the flow rate was previously determined to be \SI{2.05}{\milli\litre\per\second}.
+
+    Fig.~\ref{fig:cellOutput} shows the measured data along with the calculated power.
+    The maximum power theorem states that the maximum power
+
+    \begin{figure}
+        \begin{center}
+        \includegraphics[width=\linewidth]{graph_cellOutput}
+        \end{center}
+        \caption{Cell characteristics plotted against drawn current.
+        The cell's output }
+        \label{fig:cellOutput}
+    \end{figure}
+
+    Based on measurements of the \SI{52i}{\micro\meter} channel we estimate the amount of electrical power available for harvesting.
+    Fig.~\ref{fig:equivalentCircuit} shows the equivalent circuit for a streaming potential cell delivering a streaming current ($I_{S}$).
+    The the streaming potential ($V_{S}$) was measured with no load resistance ($R_{L}$) due to the use of the E5270 preventing load current being drawn.
+    The dimensions of the cell together with the conductivity of the working fluid give the cell an internal resistance ($R_{ch}$) of approximately \SI{30}{\giga\ohm}.
+    Using these parameters, the available output power from the cell has been calculated and is presented in Fig.~\ref{fig:cellPowerPressure} with respect to the applied pressure.
 
@@
         \end{center}
-        \caption{Estimated head loss from a mechanical water meter typically installed in a domestic setting (Kent PSMT 25mm).}
+        \caption{Estimated head loss from a mechanical water meter typically installed in a domestic setting.}
         \label{fig:headloss}
@@
         \end{center}
-        \caption{Calculated power dissipation by a typical domestic mechanical water meter (Kent PSMT 25mm) for each of the sample profile events.}
+        \caption{Calculated power dissipation by a typical domestic mechanical water meter for each of the sample profile events.}
         \label{fig:powerDissipated_meter}
@@
 
-    The Kent PSMT 25mm is a water meter typically installed in homes around the Auckland district.~\cite{WatercareNewZealand2014}.
-    Figure~\ref{fig:headloss} shows the head loss curve that we have reconstructed based on product specifications for this meter.
-    From that curve, we calculate the amount of power dissipated by the Kent PSMT meter during the average washing machine cycle, shower, and toilet flush.
-    This data is presented as figure~\ref{fig:powerDissipated_meter}.
+    Figure~\ref{fig:headloss} shows the head loss curve from a water meter typically installed at New Zealand homes (Kent PSMT 25mm).~\cite{WatercareNewZealand2014}
+    Using this pressure loss curve we calculate the amount of power dissipated by a typical water meter during an average washing machine cycle, shower, and toilet flush.
+    Calculated pressure loss due to each of these events is presented as figure~\ref{fig:powerDissipated_meter}.
     The total energy dissipated within the water meter for each of the water events is:

### 2014-10-02 graph_maxPower.py

@@ -1,0 +1,56 @@
+import os
+import sys
+import matplotlib.pyplot as plt
+
+sys.path.append('/home/mark/Dropbox/University/PhD/Workbench/electrodeInterface/')
+import lib.plot.formatter
+lib.plot.formatter.plot_params['margin']['left'] = 0.12
+lib.plot.formatter.plot_params['margin']['bottom'] = 0.09
+lib.plot.formatter.plot_params['margin']['right'] = 0.02
+lib.plot.formatter.plot_params['margin']['top'] = 0.03
+lib.plot.formatter.plot_params['ratio'] = 1
+lib.plot.formatter.format(style='IEEE')
+
+times = []
+currents = []
+pressures = []
+voltages = []
+powers = []
+with open('streamingCells_1411696812_cell9_cold_currentSweep_maxPower.csv', 'r') as f:
+    header = f.readline()
+    line = f.readline()
+    while line:
+        time, current, voltage, pressure, power = map(float,line.split(','))
+        line = f.readline()
+        times.append(time)
+        currents.append(-current)
+        voltages.append(voltage)
+        pressures.append(pressure)
+        powers.append(-power)
+
+currents = map(lambda x: x * 1e9, currents)
+
+plt.subplot(3,1,1)
+plt.gca().set_ylabel('Pressure (kPa)')
+plt.gca().set_ylim(0,300)
+plt.plot(currents, pressures, label="Pressure")
+plt.grid()
+
+plt.subplot(3,1,2)
+plt.gca().set_ylabel('Voltage (mV)$')
+plt.gca().set_ylim(0,500)
+plt.plot(currents, map(lambda x: x * 1000.0, voltages), label="Voltage")
+plt.grid()
+
+plt.subplot(3,1,3)
+plt.plot(currents, map(lambda x: x * 1.0e9, powers), label="Power")
+plt.gca().set_ylim(0,2)
+plt.gca().set_ylabel('Power (nW)')
+plt.gca().set_xlabel('Current (nA)')
+plt.grid()
+
+
+# plt.tight_layout()
+
+
+plt.savefig('graph_cellOutput.pdf', format='pdf')

### 2014-10-02 graphs.py

@@ -36,14 +36,14 @@ def func_washing(x, start=100, flow=0.122):
     cycle1_end = cycle1_start + 8.14*60.0
     cycle2_start = cycle1_end + 20*60.0
     cycle2_end = cycle2_start + 8.14*60.0
-    
+
     if cycle1_start < x < cycle1_end:
         val = flow
     elif cycle2_start < x < cycle2_end:
         val = flow
     else:
         val = 0
-        
+
     return val
 
 xs = list(range(60*60))
@@ -129,7 +129,7 @@ def pressure_loss_MPa(flow_m3_hour):
     return (0.00316*math.pow(flow_m3_hour,2) + 0.00331*flow_m3_hour + 0.00235)
 
 plt.clf()
-lib.plot.formatter.format(style='IEEE')    
+lib.plot.formatter.format(style='IEEE')
 
 xs = list(np.linspace(0,5,100))
 ys = list(map(pressure_loss_MPa, xs))
@@ -167,11 +167,12 @@ lib.plot.formatter.plot_params['margin']['left'] = 0.1
 lib.plot.formatter.plot_params['margin']['bottom'] = 0.15
 lib.plot.formatter.plot_params['margin']['right'] = 0.026
 lib.plot.formatter.plot_params['margin']['top'] = 0.03
-lib.plot.formatter.format(style='IEEE')    
+lib.plot.formatter.format(style='IEEE')
 plt.gca().set_xlabel('Channel height ($\mu$m)')
 plt.gca().set_ylabel('Voltage-pressure gradient ($\mu$V/Pa)')
-plt.scatter(height,slope, color="black", edgecolor=None, s=5)
+plt.scatter(height,slope, marker='o', facecolor='blue', edgecolor='blue', s=8)
 plt.gca().set_xlim(0,250)
+plt.gca().set_ylim(0,1.201)
 plt.grid()
 plt.savefig('graph_cellEfficiency.pdf', format='pdf')
 
@@ -234,11 +235,11 @@ lib.plot.formatter.plot_params['margin']['left'] = 0.11
 lib.plot.formatter.plot_params['margin']['bottom'] = 0.15
 lib.plot.formatter.plot_params['margin']['right'] = 0.026
 lib.plot.formatter.plot_params['margin']['top'] = 0.03
-lib.plot.formatter.format(style='IEEE')    
+lib.plot.formatter.format(style='IEEE')
 plt.gca().set_xlabel('Pressure (kPa)')
[…]

### 2014-10-02 paper.tex
Proofread & edited

@@
 
-\author{Mark~H.~Jones, and Jonathan~Scott}
+\author{Mark~H.~Jones and Jonathan~Scott}
 
@@
     Cheap and reliable methods of retrieving meter data is an important consideration for utility companies.
-    The introduction of wireless automatic meter readers offers many advantages to town water suppliers.
-    These advantages include reductions in cost and error rates associated with collecting metering data, increased billing frequency, leak detection and the elimination of the need for meter readers to access the consumers property.~\cite{Chang2012,Britton2013}
+    The introduction of wireless automatic meter readers offers many advantages to suppliers of town water.
+    These advantages include reductions in cost and error rates associated with collecting metering data, increased billing frequency, leak detection and the elimination of the need for meter readers to access the consumers' property.~\cite{Chang2012,Britton2013}
 
-    The location of a typical water water meter means electrical power is usually provided by long life batteries.
-    The batteries used in automatic meter readers are non-rechargeable and have a life-span of 10 years.\cite{BMeters2014}
+    The location of a typical water meter means electrical power is usually provided by long life batteries.
+    The batteries used in automatic meter readers are non-rechargeable and have a life-span of 10 years.~\cite{BMeters2014}
     The possibility of harvesting energy at the meter should allow frequent data reporting with less maintenance.
@@
 
-    Streaming cells provide a way of converting fluid energy into electrical energy.
+    Streaming cells provide a way of converting fluid energy into electrical energy without moving parts.
     They work on the principle that charged surfaces in contact with ionic solutions attract counter-ions\footnote{The terms counter-ion and co-ion refer to ions of opposite and like charge relative to the polarity of the solid surface respectively.} so as to form a charged layer at the contact surface.~\cite{Stein2004}
     This charged layer is termed the double layer and is the key mechanism that enables streaming cell energy conversion.
-    It is possible to pump and collect ions from withing the double layer with the application of pressure.
+    The conversion is made by forcing ions within the double layer through narrow channels with the application of hydrostatic pressure.
 
-    A double layer is called such because it is made of two inividual layers; the Stern and diffuse layers.
-    % A double layer can be broken into two sub-layers; the Stern and diffuse layers.
-    The Stern layer is comprised of immobilised ions situated very close the charged solid surface.~\cite{Salieb-Beugelaar2009}
-    The diffuse layer is formed by the ions attracted to the surface, but not so strongly as to be immobile.
+    A double layer is called such because it is made of two individual layers; the Stern and diffuse layers.
+    The Stern layer is comprised of immobilised ions situated at the charged solid surface.~\cite{Salieb-Beugelaar2009}
+    The diffuse layer surrounds the Stern layer where counter-ions are not so strongly bound as to be immobile.
     A streaming cell moves ions in the diffuse layer through one or more narrow channels, concentrating them on the other side.
@@
     Channels can also be formed en-mass by using porous materials such as glass or ceramics as the cell where the pores themselves form channels.
-    When using glass, the surface spontaneously develops a negative surface charge when it comes in contact with water.
-    The charge is caused by deprotonation at the contact surface (SiOH~$\leftrightarrows$~SiO$^{-}+$~H$^{+}$).
-    By immersing a channel in an electrolyte solution double layers line the interior walls of the channel.
-    The thickness of this layer is defined by the Debye length ($l_{D}$) and is controlled the ionic concentration of the liquid.~\cite{Israelachvili2011}
+    Glass has the attractive property that it obtains a negative surface charge when in contact with water.
+    This surface charge is caused by the deprotonation of surface silanol groups in glass (SiOH~$\leftrightarrows$~SiO$^{-}+$~H$^{+}$).~\cite{Kirby2004a}
+    By immersing a glass channel in an electrolyte solution, double layers of positive ions occupy the interior walls of the channel.
+    The thickness of the double layer is defined as the Debye length ($l_{D}$) and is controlled the ionic concentration of the liquid.~\cite{Israelachvili2011}
 
-    When the dimensions of a channel become small the double layers begin to overlap and co-ions are repelled from the channel.
-    Counter-ions within a streaming cell are collected by applying a pressure gradient across the channel/cell.
-    Pressure forces the liquid through the channel (from which co-ions have been removed) creating a streaming current.
-    It is the streaming current that raises the voltage (streaming potential) across the cell as the ions are pumped through it.
+    When the dimensions of a channel become small enough, double layers will overlap.
+    Overlapping double layers mean that co-ions are repelled from within the channel.
+
+    Counter-ions within a streaming cell are transported by applying a pressure gradient across the channel/cell.
+    Pressure forces the counter-ion rich fluid through the channel creating a streaming current.
+    Streaming currents establish a voltage across the cell, termed streaming potential, due to ionic concentrations at each end of the channel becoming unbalanced.
 
     Streaming currents have been heavily investigated as a means of generating electrical energy from pressure gradients.~\cite{Chang2009,Daiguji2006,Daiguji2004b,Davidson2008a,Davidson2008,CherngHon2012,Jiao2014,Lu2006,Olthuis2005,Osterle1964,Pennathur2007,Ren2008a,VanderHeyden2006,Heyden2007,Xie2008,Yang2003}
-    % It is expected that a channel height equal to twice the Debye length leads to maximum energy conversion efficiency.~\cite{Daiguji2004b}
     Theoretical predictions of the efficiency of standard micro/nano-fluidic channels are 2\% for pure water and 7\% for sodium chloride.~\cite{VanderHeyden2006}
@@
 
-    \section{Readily Attainable Streaming Cell Power} \label{sect:streamingCell}
+    \section{Readily Attainable Streaming Cell Efficiency} \label{sect:streamingCell}
     \begin{figure}
@@
     In~\cite{Gu2000}, the authors employ a relatively simple parallel plate design to create a streaming cell.
-    They glued plastic shims between parallel plates of glass, providing a simple way of controlling channel height.
+    They glued plastic shims between parallel plates of glass, providing a simple way of setting a channel's height.
     Using that method, the authors fabricated three cells with channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
@@
     Pressure is applied across each cell by connecting one end to a tap and leaving the other open to atmosphere.
-    A Honeywell pressure sensor (model 26PC15SMT) is connected across the input/output tubes to measure the developed pressure differential.
-    An Agilent precision measurement mainframe (model E5270B) is used to measure streaming potential and read the pressure sensor's output.
-    The working fluid, being tap water, had a conductivity of \SI{1.87e-6}{\siemens\per\meter} as measured with an EDT Instruments RE 388Tx Conductivity Meter.
+    A Honeywell pressure sensor (model 26PC15SMT) is placed across the cell to measure applied pressure.
+    An Agilent precision measurement mainframe (model E5270B) is used to measure streaming potential, streaming current and to read the pressure sensor's output.
+    The working fluid, being tap water, had a conductivity of \SI{183e-6}{\siemens\per\meter} as measured with an EDT Instruments RE 388Tx Conductivity Meter.
 
-    Measured pressure-to-voltage gradients from each of the ten streaming cells is presented in Fig.~\ref{fig:cellEfficiency}.
-    We put the spread in data points down to asymmetry in the cells and uncertainty of the internal dimensions.
-    When viewed under the microscope the opposite ends of cell heights differing as much as \SI{3}{\micro\meter} in some cases.
+    Measured pressure-to-voltage gradients from each of the ten streaming cells are presented in Fig.~\ref{fig:cellEfficiency}.
+    Spread in the data suggests uncertainty in the internal dimensions of each cell.
     Due to the opacity of the resin used, measurement of the internal cell dimensions was not possible.
-
-    The plot shows a loose relationship between channel height and voltage gradient per Pascal of applied pressure.
-    The cell with height \SI{26}{\micro\meter} shows a much lower slope, probably as a result of a reduced flow rate.
-    We were unable to measure the flow rate of the \SI{26}{\micro\meter} cell before it burst.
+    The plot shows the relationship between channel height and voltage gradient per Pascal of applied pressure.
+    Each cell had a different flow rate, which this plot does not take into account.
+    Three of the cells bust before flow measurements were obtained.
+    % The \SI{26}{\micro\meter} channel shows a much lower gradient due to . which we expect is a result of a reduced flow rate.
+    % The \SI{26}{\micro\meter} cell burst before we obtained flow rate measurements.
 
@@
     We now measure available power output of the \SI{71}{\micro\meter} streaming cell.
-    This cell was chosen as the \SI{52}{\micro\meter} cell burst during operation and the \SI{71}{\micro\meter} cell seemed an appropriate substitute as per Fig.~\ref{fig:cellEfficiency}.
-    We measure the streaming voltage, and pressure, while sweeping the amount of electrical current drawn from the device.
+    This cell was chosen as it remained mechanically robust and had good output characteristics.
+    We measure the streaming voltage and pressure while sweeping the electrical current draw from the device.
     The applied pressure was held at \SI{260}{\kilo\pascal} for the duration of the measurement and the flow rate was previously determined to be \SI{2.05}{\milli\litre\per\second}.
 
-    Fig.~\ref{fig:cellOutput} shows the measured data along with the calculated power.
-    The maximum power theorem states that the maximum power
+    Fig.~\ref{fig:cellOutput} shows the measured data along with the calculated power curve.
+    Using the power curve we calculate the cell's internal electrical resistance to be \SI{5.6}{\mega\ohm}.
+    Peak output power of \SI{1.52}{\nano\watt} is delivered when the current draw is \SI{33.5}{\nano\ampere} with a voltage of \SI{182}{\milli\volt}.
+
+    Based on the pressure applied and the flow rate through the cell, the input power is \SI{539}{\milli\watt}.
+    Energy conversion efficiency is in the order of $1\times 10^{-6}\%$.
 
@@
         \end{center}
-        \caption{Cell characteristics plotted against drawn current.
-        The cell's output }
+        \caption{Streaming cell output voltage as a function of drawn current with constant pressure.
+        The cell's calculated output power appears in the lower plot with a peak at approximately \SI{33.5}{\nano\ampere}.}
         \label{fig:cellOutput}
@@
 
-    Based on measurements of the \SI{52i}{\micro\meter} channel we estimate the amount of electrical power available for harvesting.
-    Fig.~\ref{fig:equivalentCircuit} shows the equivalent circuit for a streaming potential cell delivering a streaming current ($I_{S}$).
-    The the streaming potential ($V_{S}$) was measured with no load resistance ($R_{L}$) due to the use of the E5270 preventing load current being drawn.
-    The dimensions of the cell together with the conductivity of the working fluid give the cell an internal resistance ($R_{ch}$) of approximately \SI{30}{\giga\ohm}.
-    Using these parameters, the available output power from the cell has been calculated and is presented in Fig.~\ref{fig:cellPowerPressure} with respect to the applied pressure.
+    % Based on measurements of the \SI{52i}{\micro\meter} channel we estimate the amount of electrical power available for harvesting.
+    % Fig.~\ref{fig:equivalentCircuit} shows the equivalent circuit for a streaming potential cell delivering a streaming current ($I_{S}$).
+    % The the streaming potential ($V_{S}$) was measured with no load resistance ($R_{L}$) due to the use of the E5270 preventing load current being drawn.
+    % The dimensions of the cell together with the conductivity of the working fluid give the cell an internal resistance ($R_{ch}$) of approximately \SI{30}{\giga\ohm}.
+    % Using these parameters, the available output power from the cell has been calculated and is presented in Fig.~\ref{fig:cellPowerPressure} with respect to the applied pressure.
 
-    \begin{figure}
-        \begin{center}
-        \includegraphics[width=\linewidth]{StreamingCell_EquivalentCircuit}
-        \end{center}
-        \caption{Equivalent circuit of the streaming potential cell.
-        Streaming current is produced by the current source and is denoted $I_{S}$.
-        The internal channel resistance is $R_{ch}$ and an external load is denoted as $R_{L}$}
-        \label{fig:equivalentCircuit}
-    \end{figure}
-
-    \begin{figure}
-        \begin{center}
-        \includegraphics[width=\linewidth]{graph_powerPressure}
-        \end{center}
-        \caption{Maximum power available to an external load placed across the \SI{52}{\micro\meter} cell as a function of pressure differential.
+    % \begin{figure}
+    %     \begin{center}
+    %     \includegraphics[width=\linewidth]{graph_powerPressure}
+    %     \end{center}
+    %     \caption{Maximum power available to an external load placed across the \SI{52}{\micro\meter} cell as a function of pressure differential.
 Power has been calculated using a load resistance of \SI{30}{\giga\ohm} where only half of total power is available to the load.
 Note that the units of power are expressed in picoWatts.}
-        \label{fig:cellPowerPressure}
-    \end{figure}
+    %     \label{fig:cellPowerPressure}
+    % \end{figure}
 
@@
 
-    Figure~\ref{fig:headloss} shows the head loss curve from a water meter typically installed at New Zealand homes (Kent PSMT 25mm).~\cite{WatercareNewZealand2014}
-    Using this pressure loss curve we calculate the amount of power dissipated by a typical water meter during an average washing machine cycle, shower, and toilet flush.
-    Calculated pressure loss due to each of these events is presented as figure~\ref{fig:powerDissipated_meter}.
-    The total energy dissipated within the water meter for each of the water events is:
+    Figure~\ref{fig:headloss} shows the pressure head loss curve from a water meter typically installed at New Zealand homes (Kent PSMT 25mm).~\cite{WatercareNewZealand2014}
+    Using this curve we calculate power dissipation in a water meter during a washing machine cycle, shower, and toilet flush; presented as Fig.~\ref{fig:powerDissipated_meter}
+    The total energy dissipated within the meter for each events is:
     \begin{itemize}
@@
 
-    \section{Estimation of Power Requirements}
+    \section{Estimation of Energy Requirements}
     \label{sect:powerRequirements}
     In \cite{Jones2011} we measure the energy efficiency of various low-power microcontrollers.
-    Here we take measured data from that paper to estimate processor energy requirements.
+    Here we take measured data from that paper to estimate a smart meter's energy requirements.
     Measurements of an Atmel ATtiny 25V have been used as it offered good performance over a wide range of processor functions.
@@
 
-    The energy requirements for a 100 byte data transmission over ZigBee (Digi International XBee S2) is presented as Fig.~\ref{fig:xbeePower}.
-    This measurement was recorded using a Tektronix TDC 2012 Digital Storage Oscilloscope across a \SI{10.2}{\ohm} current sense resistor.
+    The energy requirements for a 100 byte data transmission over ZigBee (Digi International XBee S2) is presented as Fig.~\ref{fig:xbeePower} (recorded using a Tektronix TDC 2012 Digital Storage Oscilloscope across a \SI{10.2}{\ohm} current sense resistor).
 
-    Our figures show a monitoring and transmitting device needs \SI{6.96}{\joule} per day to operate in ideal transmission conditions.
+    Our estimation shows a monitoring and transmitting device would need about \SI{6.96}{\joule} per day to operate in ideal transmission conditions.
     If the transmitter were to require $100\times$ more energy to transmit, as an estimate of poor conditions, the energy requirements would jump to \SI{9.39}{\joule} per day.
@@
 
-    \section{Estimation of Streaming Cell Harvester}
-    \label{sect:harvesterSize}
-    We have estimated that a harvester would need to harvest approximately \SI{10}{\joule} of energy per day.
-    We have calculated that approximately \SI{1}{\kilo\joule} of energy is dissipated per day inside a typical water meter at a two occupant dwelling.
-    Therefore we predict that a harvester needs to capture only 1\% of the energy lost in a typical domestic water meter in order to operate a basic smart metering device.
+    % \section{Estimation of Streaming Cell Harvester}
+    % \label{sect:harvesterSize}
+    \section{Conclusion}
+    We have calculated approximately \SI{1}{\kilo\joule} of energy is dissipated per day inside a typical water meter at a two occupant dwelling.
+    We have estimated that a harvester would need to harvest approximately \SI{10}{\joule} of energy per day to record and transmit water consumption data.
+    Therefore an energy harvester with an energy conversion efficiency of 1\% is required.
+    Streaming cells we constructed produced conversion efficiencies in the order of $1\times 10^{-6}\%$.
 
-    \section{Conclusion}
+    % \section{Conclusion}
     \bibliographystyle{plain}

### 2014-10-02 datafiles/graph_maxPower.py

@@ -1,0 +1,56 @@
+import os
+import sys
+import matplotlib.pyplot as plt
+
+sys.path.append('/home/mark/Dropbox/University/PhD/Workbench/electrodeInterface/')
+import lib.plot.formatter
+lib.plot.formatter.plot_params['margin']['left'] = 0.09
+lib.plot.formatter.plot_params['margin']['bottom'] = 0.15
+lib.plot.formatter.plot_params['margin']['right'] = 0.02
+lib.plot.formatter.plot_params['margin']['top'] = 0.03
+lib.plot.formatter.plot_params['ratio'] = 1
+lib.plot.formatter.format(style='IEEE')
+
+times = []
+currents = []
+pressures = []
+voltages = []
+powers = []
+with open('streamingCells_1411696812_cell9_cold_currentSweep_maxPower.csv', 'r') as f:
+    header = f.readline()
+    line = f.readline()
+    while line:
+        time, current, voltage, pressure, power = map(float,line.split(','))
+        line = f.readline()
+        times.append(time)
+        currents.append(-current)
+        voltages.append(voltage)
+        pressures.append(pressure)
+        powers.append(-power)
+
+currents = map(lambda x: x * 1e9, currents)
+
+plt.subplot(3,1,1)
+plt.gca().set_ylabel('Pressure $(kPa)$')
+plt.gca().set_ylim(0,300)
+plt.plot(currents, pressures, label="Pressure")
+plt.grid()
+
+plt.subplot(3,1,2)
+plt.gca().set_ylabel('Voltage $(mV)$')
+plt.gca().set_ylim(0,500)
+plt.plot(currents, map(lambda x: x * 1000.0, voltages), label="Voltage")
+plt.grid()
+
+plt.subplot(3,1,3)
+plt.plot(currents, map(lambda x: x * 1.0e9, powers), label="Power")
+plt.gca().set_ylim(0,2)
+plt.gca().set_ylabel('Power $(nW)$')
+plt.gca().set_xlabel('Current $(nA)$')
+plt.grid()
+
+
+plt.tight_layout()
+
+
+plt.savefig('Output power', format='pdf')

### 2014-10-02 datafiles/process.py

@@ -1,0 +1,67 @@
+import os
+import sys
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib.pyplot as plt
+
+filenames = os.listdir('.')
+filenames = filter(lambda x: x.find('_cold_'),filenames)
+# print(filenames)
+filenames = filter(lambda x: x[-4:] == '.csv', filenames)
+filenames.sort()
+
+pp = PdfPages('all.pdf')
+
+for filename in filenames:
+    times = []
+    currents = []
+    pressures = []
+    voltages = []
+    powers = []
+    with open(filename, 'r') as f:
+        header = f.readline()
+        line = f.readline()
+        while line:
+            time, current, voltage, pressure, power = map(float,line.split(','))
+            line = f.readline()
+            times.append(time)
+            if filename.find('currentSweep') != -1:
+                current = abs(current)
+                power = abs(power)
+            currents.append(current)
+            voltages.append(voltage)
+            pressures.append(pressure)
+            powers.append(power)
+
+    plt.clf()
+    plt.subplot(4,1,1)
+    plt.title(filename[26:-4])
+
+    plt.gca().set_ylabel('Current')
+    plt.gca().set_ylim(0,1e-7)
+    plt.plot(times, currents, label="Current")
+    plt.grid()
+
+    plt.subplot(4,1,2)
+    plt.gca().set_ylabel('Voltage')
+    plt.gca().set_ylim(0,0.5)
+    plt.plot(times, voltages, label="Voltage")
+    plt.grid()
+
+    plt.subplot(4,1,3)
+    plt.gca().set_ylabel('Pressure')
+    plt.gca().set_ylim(0,300)
+    plt.plot(times, pressures, label="Pressure")
+    plt.grid()
+
+    plt.subplot(4,1,4)
+    plt.plot(times, powers, label="Power")
+    plt.gca().set_ylim(0,1e-8)
+    plt.gca().set_ylabel('Power')
+    plt.grid()
+
+
+    plt.tight_layout()
+
+
+    plt.savefig(pp, format='pdf')
+pp.close()

### 2014-10-03 paper.tex
Friday morning changes

@@
 \usepackage{siunitx}
-% \usepackage[dvipsnames]{color}
+\usepackage[dvipsnames]{color}
 
@@
     \begin{abstract}
-        We investigate the possibility of using streaming cells as a means of harvesting energy from a town water supply.
-        We verify streaming cell measurements found in the literature and extend those measurements over a wider range of dimensions.
-        We measure the electrical power developed streaming cells using town water.
+        We investigate the possibility of using streaming cells as a means of harvesting energy from the town water supply.
+        We measure the electrical power developed from streaming cells using tap water.
+        We estimate the amount of energy available from a typical domestic household based on water usage data.
         We estimate the amount of energy required to operate a simple data logger and transmitter.
-        We estimate the amount of energy available from a typical domestic household based on water usage data.
-        From these estimates we calculate minimum geometric dimensions required to deliver practical power output to a wireless water meter.
-        Finally, we comment on the feasibility of using streaming cell technology as a means of harvesting energy from a domestic water supply.
+        From these estimates we calculate the required efficiency and physical form of a streaming cell energy converter.
+        We comment on the feasibility of using streaming cell technology as a means of harvesting energy from a domestic water supply.
     \end{abstract}
@@
     Domestic and commercial water metering is becoming increasingly common throughout the world.~\cite{Chang2012}
-    Cheap and reliable methods of retrieving meter data is an important consideration for utility companies.
+    Cheap and reliable methods of retrieving metered data is an important consideration for utility companies.
+
     The introduction of wireless automatic meter readers offers many advantages to suppliers of town water.
-    These advantages include reductions in cost and error rates associated with collecting metering data, increased billing frequency, leak detection and the elimination of the need for meter readers to access the consumers' property.~\cite{Chang2012,Britton2013}
+    These advantages include reduced error rates associated with collecting data, increased billing frequency, leak detection and the elimination of the need for meter readers to access the consumers' property.~\cite{Chang2012,Britton2013}
 
@@
     Streaming cells provide a way of converting fluid energy into electrical energy without moving parts.
-    They work on the principle that charged surfaces in contact with ionic solutions attract counter-ions\footnote{The terms counter-ion and co-ion refer to ions of opposite and like charge relative to the polarity of the solid surface respectively.} so as to form a charged layer at the contact surface.~\cite{Stein2004}
+    They work on the principle that charged surfaces in contact with ionic solutions attract counter-ions so as to form a charged layer at the contact surface.~\cite{Stein2004}
     This charged layer is termed the double layer and is the key mechanism that enables streaming cell energy conversion.
@@
 
+    \begin{figure}
+        \begin{center}
+        \includegraphics{diagram_streamingCellPrinciple}
+        \end{center}
+        \caption{Conceptualised rendering of the cross section of a streaming cell.
+        Positive ions are being forced through the cavity by the application of pressure.}
+        \label{fig:streamingPrinciple}
+    \end{figure}
+
     A double layer is called such because it is made of two individual layers; the Stern and diffuse layers.
-    The Stern layer is comprised of immobilised ions situated at the charged solid surface.~\cite{Salieb-Beugelaar2009}
-    The diffuse layer surrounds the Stern layer where counter-ions are not so strongly bound as to be immobile.
-    A streaming cell moves ions in the diffuse layer through one or more narrow channels, concentrating them on the other side.
+    The Stern layer is comprised of immobilised ions at the charged solid surface.~\cite{Salieb-Beugelaar2009}
+    The diffuse layer surrounds the Stern layer and contains counter-ions that are not so strongly bound as to be immobile.
+    The thickness of the double layer is defined as the Debye length ($l_{D}$) and is dependant upon the ionic concentration of the liquid.~\cite{Israelachvili2011}
+    When the dimensions of a channel become small enough, double layers will overlap.
+    Overlapping double layers mean that any co-ions are repelled from within the channel.
 
-    Streaming cell channels can be created individually using a range fabrication methods, such as chemical etching or the use of narrowly separated parallel plates.
+    The channels can be created individually using a range fabrication methods, such as chemical etching or the use of narrowly separated parallel plates.
     Channels can also be formed en-mass by using porous materials such as glass or ceramics as the cell where the pores themselves form channels.
@@
     This surface charge is caused by the deprotonation of surface silanol groups in glass (SiOH~$\leftrightarrows$~SiO$^{-}+$~H$^{+}$).~\cite{Kirby2004a}
-    By immersing a glass channel in an electrolyte solution, double layers of positive ions occupy the interior walls of the channel.
-    The thickness of the double layer is defined as the Debye length ($l_{D}$) and is controlled the ionic concentration of the liquid.~\cite{Israelachvili2011}
-
-    When the dimensions of a channel become small enough, double layers will overlap.
-    Overlapping double layers mean that co-ions are repelled from within the channel.
+    By immersing a glass channel in an electrolyte solution, double layers of positive ions (counter-ions in this case) occupy the interior walls of the channel.
 
@@
     \end{itemize}
-    These results indicate that solutions containing salt are more efficient as a working liquid, however the maximum efficiency is found when the salt concentration is low.~\cite{VanderHeyden2006}
+    These results indicate that small channels using solutions containing salt are more efficient.
+    According to \cite{Daiguji2004b}, the efficiency is maximised when the channel height is about half the Debye length.
+    For water with a sodium content in the range 1--100~ppm this equates to a channel height in the order of 100--10~nm.
+    Additionally, ~\cite{VanderHeyden2006} states that the maximum efficiency is found when the salt concentration is low.
 
@@
     This type of enhancement would overcome the `no-slip boundary condition' at the solid-liquid interface.
-    Slip at the interface boundary would mean that ions in the Stern layer, where ionic concentration is highest, could also be moved across the channel.
+    Slip at the interface boundary would mean that ions in the Stern layer, where ionic concentration is highest, could also be moved through the channel.
     Surface enhanced channels are out of the scope of this study due to cost and manufacturing difficulty.
-
-    % In~\cite{Joly2006} it is suggested that a polarised hydrophobic surface would strongly enhance electro-osmotic effects and therefore further increase conversion efficiency
 
@@
     The remainder of this work is presented as follows.
-    In section \ref{sect:streamingCell} we build and measure a simple streaming potential cell.
+    In section \ref{sect:streamingCell} we build, measure and calculate the conversion efficiency of a simple streaming potential cell.
     We confirm the relationship between pressure and applied pressure and investigate the effect of channel height.
-    In section \ref{sect:waterConsumption} we estimate the amount of harvestable energy from a constructed domestic water usage profile.
+    In section \ref{sect:waterConsumption} we estimate the amount of harvestable energy from a domestic water usage profile.
     Section \ref{sect:powerRequirements} quantifies energy requirements of a simple electronic meter.
-    Following on this, section \ref{sect:harvesterSize} presents the required cell dimensions of a harvester capable of producing the requisite energy.
-    In section \ref{sect:results} we combine and present results of our measurements and quantify our predictions.
     And finally, we conclude with a discussion on the feasibility of using streaming cells to harvest energy.
@@
 
-    We replicate the approximate dimensions of \cite{Gu2000} to produce ten streaming cells (\SI{245}{\micro\meter}, \SI{178}{\micro\meter}, \SI{161}{\micro\meter}, \SI{125}{\micro\meter}, \SI{106}{\micro\meter}, \SI{75}{\micro\meter}, \SI{71}{\micro\meter}, \SI{56}{\micro\meter}, \SI{52}{\micro\meter}, \SI{26}{\micro\meter}).
+    We replicate the approximate dimensions of \cite{Gu2000} to produce ten streaming cells.
+    The approximate internal channel heights of these channels are \SI{245}{\micro\meter}, \SI{178}{\micro\meter}, \SI{161}{\micro\meter}, \SI{125}{\micro\meter}, \SI{106}{\micro\meter}, \SI{75}{\micro\meter}, \SI{71}{\micro\meter}, \SI{56}{\micro\meter}, \SI{52}{\micro\meter}, and \SI{26}{\micro\meter}.
     The channels are made from glass microscope slides (Sail Brand - JIA 7101WT) sectioned into halves.
@@
 
-    Pressure is applied across each cell by connecting one end to a tap and leaving the other open to atmosphere.
+    Pressure is applied to the cell by connection to tap and leaving the output connection open to atmosphere.
     A Honeywell pressure sensor (model 26PC15SMT) is placed across the cell to measure applied pressure.
@@
     Measured pressure-to-voltage gradients from each of the ten streaming cells are presented in Fig.~\ref{fig:cellEfficiency}.
-    Spread in the data suggests uncertainty in the internal dimensions of each cell.
+    Spread in the data is attributed to uncertainty in the internal dimensions of each cell.
     Due to the opacity of the resin used, measurement of the internal cell dimensions was not possible.
@@
     Each cell had a different flow rate, which this plot does not take into account.
-    Three of the cells bust before flow measurements were obtained.
+    Three of the cells burst before flow measurements were obtained.
     % The \SI{26}{\micro\meter} channel shows a much lower gradient due to . which we expect is a result of a reduced flow rate.
@@
     \label{sect:waterConsumption}
+
+    % \begin{figure}
+    %     \begin{center}
+    %     \includegraphics[width=\linewidth]{graph_profile}
+    %     \includegraphics[width=\linewidth]{graph_pressureLoss}
+    %     \includegraphics[width=\linewidth]{graph_harvest}
+    %     \end{center}
+    %     \caption{
+    %     Calculation of the power dissipation inside a typical water meter.
+    %     The top figure shows flow profiles for one washing machine use, a shower and a toilet flush in a typical dwelling.
+    %     Underneath is the head loss curve from a typical domestic water meter as a function of flow rate.
+    %     The lower figure presents each of the water usage events (shower, washing machine and toilet flush) in terms of power dissipated inside the water meter due to mechanical losses.
+    %     Dissipated power is calculated from the head loss curve and the flow rate data of the upper graphs.
+    %     }
+    %     \label{fig:profileSample}
+    % \end{figure}
+
     \begin{figure}
@@
     % \label{sect:harvesterSize}
+
     \section{Conclusion}
+    \label{sect:conclusion}
     We have calculated approximately \SI{1}{\kilo\joule} of energy is dissipated per day inside a typical water meter at a two occupant dwelling.

### 2014-10-03 paper.tex
Start estimating harvester size

@@
     Energy conversion efficiency is in the order of $1\times 10^{-6}\%$.
+    While the conversion efficiency is much lower than those stated in the introduction, we use much larger channel dimensions and use tap water as our working fluid.
 
@@
 
-    % \section{Estimation of Streaming Cell Harvester}
-    % \label{sect:harvesterSize}
+    \section{Sizing of Streaming Cell Harvester}
+    \label{sect:harvesterSize}
+    In order to achieve the target conversion efficiency of 1\% the internal channel height must be reduced to something in the order of \SI{1}{\micro\meter}--\SI{10}{\nano\meter}.
 
@@
     \label{sect:conclusion}
-    We have calculated approximately \SI{1}{\kilo\joule} of energy is dissipated per day inside a typical water meter at a two occupant dwelling.
+    Approximately \SI{1}{\kilo\joule} of energy is dissipated per day inside a typical water meter at a two occupant dwelling.
     We have estimated that a harvester would need to harvest approximately \SI{10}{\joule} of energy per day to record and transmit water consumption data.

### 2014-10-04 paper.tex
Night work

@@
     These results indicate that small channels using solutions containing salt are more efficient.
-    According to \cite{Daiguji2004b}, the efficiency is maximised when the channel height is about half the Debye length.
+    According to \cite{Daiguji2004b}, the efficiency is maximised when the channel height twice that of the Debye length.
     For water with a sodium content in the range 1--100~ppm this equates to a channel height in the order of 100--10~nm.
@@
     \label{sect:harvesterSize}
-    In order to achieve the target conversion efficiency of 1\% the internal channel height must be reduced to something in the order of \SI{1}{\micro\meter}--\SI{10}{\nano\meter}.
+    We now estimate the physical size of a harvester capable of supplying the energy to run a wireless water meter.
+    Auckland tap water has a sodium content of 2.1--26.0\thinspace mg/L.~\cite{WatercareNewZealand2012}
+    This equates to a Debye length in the range 0.3--\SI{1.0}{\nano\meter} and the optimum channel height between 0.6--\SI{2.1}{\nano\meter}.
+    This gap is negligible compared to the thickness of the glass substrate required to create such a harvester, which we presume to be \SI{1}{\milli\meter}.
+    The harvester would be made from stacked glass substrates, each separated by a dimension that provides the target 1\% efficiency.
+    For simplicity we constrain the dimensions of the channel ends to be square, i.e. the width of the channels will equal the height of the stack.
+    The length of the channels in the stack will be \SI{1}{\centi\meter}.
 

### 2014-10-06 paper.tex
Final edits

--- 2014-10-03 paper.tex
@@
         We investigate the possibility of using streaming cells as a means of harvesting energy from the town water supply.
-        We measure the electrical power developed from streaming cells using tap water.
+        We measure the electrical power developed from streaming cells using tap water as a working fluid.
         We estimate the amount of energy available from a typical domestic household based on water usage data.
@@
     \section{Introduction}
+    \label{sect:Introduction}
     Domestic and commercial water metering is becoming increasingly common throughout the world.~\cite{Chang2012}
-    Cheap and reliable methods of retrieving metered data is an important consideration for utility companies.
+    Cheap and reliable methods for retrieving metered data are important for water utility companies.
 
-    The introduction of wireless automatic meter readers offers many advantages to suppliers of town water.
-    These advantages include reduced error rates associated with collecting data, increased billing frequency, leak detection and the elimination of the need for meter readers to access the consumers' property.~\cite{Chang2012,Britton2013}
+    The introduction of wireless automatic meter reading systems offers many advantages to suppliers of town water.
+    These include increased billing frequency, leak detection and removal of the need to access consumers' property.~\cite{Chang2012,Britton2013}
 
     The location of a typical water meter means electrical power is usually provided by long life batteries.
-    The batteries used in automatic meter readers are non-rechargeable and have a life-span of 10 years.~\cite{BMeters2014}
-    The possibility of harvesting energy at the meter should allow frequent data reporting with less maintenance.
-    Removing the batteries from current meter reading systems should reduce both the total cost of ownership and electrical waste.
+    The batteries used in automatic meter readers are non-rechargeable and have a life-span of around 10 years.~\cite{BMeters2014}
+    Removing batteries from meter reading systems will reduce both the total cost of ownership and electrical waste.
 
@@
     They work on the principle that charged surfaces in contact with ionic solutions attract counter-ions so as to form a charged layer at the contact surface.~\cite{Stein2004}
-    This charged layer is termed the double layer and is the key mechanism that enables streaming cell energy conversion.
-    The conversion is made by forcing ions within the double layer through narrow channels with the application of hydrostatic pressure.
+    This charged layer is termed the interfacial double layer and is the key mechanism that enables streaming cell energy conversion.
+    The conversion is made by forcing ions within the double layer through narrow channels by applying hydrostatic pressure.
 
@@
 
-    A double layer is called such because it is made of two individual layers; the Stern and diffuse layers.
-    The Stern layer is comprised of immobilised ions at the charged solid surface.~\cite{Salieb-Beugelaar2009}
+    A double layer is comprised of two individual layers; the Stern and diffuse layers.
+    The Stern layer refers to immobilised counter-ions bound directly to the liquid-solid interface.~\cite{Salieb-Beugelaar2009}
     The diffuse layer surrounds the Stern layer and contains counter-ions that are not so strongly bound as to be immobile.
     The thickness of the double layer is defined as the Debye length ($l_{D}$) and is dependant upon the ionic concentration of the liquid.~\cite{Israelachvili2011}
-    When the dimensions of a channel become small enough, double layers will overlap.
+    When the dimensions of a streaming cell channel become small enough, double layers will overlap.
     Overlapping double layers mean that any co-ions are repelled from within the channel.
+    A simplified diagram showing counter-ions being forced through a streaming cell channel is presented as Fig.~\ref{fig:streamingPrinciple}.
 
-    The channels can be created individually using a range fabrication methods, such as chemical etching or the use of narrowly separated parallel plates.
-    Channels can also be formed en-mass by using porous materials such as glass or ceramics as the cell where the pores themselves form channels.
+    Channels can be created individually using a range fabrication methods, such as chemical etching or using narrowly separated parallel plates.
+    They can also be formed en-mass by using porous materials such as glass or ceramics, where the pores themselves act as channels.
+
     Glass has the attractive property that it obtains a negative surface charge when in contact with water.
     This surface charge is caused by the deprotonation of surface silanol groups in glass (SiOH~$\leftrightarrows$~SiO$^{-}+$~H$^{+}$).~\cite{Kirby2004a}
-    By immersing a glass channel in an electrolyte solution, double layers of positive ions (counter-ions in this case) occupy the interior walls of the channel.
+    By immersing a glass channel in an electrolyte solution, double layers of counter-ions (positive ions in this case) occupy the interior walls of the channel.
 
-    Counter-ions within a streaming cell are transported by applying a pressure gradient across the channel/cell.
-    Pressure forces the counter-ion rich fluid through the channel creating a streaming current.
+    Counter-ions within a streaming cell are transported by applying a pressure gradient across the channel.
+    Pressure forces the counter-ion rich fluid through the channel creating a current of ions, termed the streaming current.
     Streaming currents establish a voltage across the cell, termed streaming potential, due to ionic concentrations at each end of the channel becoming unbalanced.
@@
     These results indicate that small channels using solutions containing salt are more efficient.
-    According to \cite{Daiguji2004b}, the efficiency is maximised when the channel height is about half the Debye length.
-    For water with a sodium content in the range 1--100~ppm this equates to a channel height in the order of 100--10~nm.
+    According to \cite{Daiguji2004b}, the efficiency is maximised when the channel height twice that of the Debye length.
     Additionally, ~\cite{VanderHeyden2006} states that the maximum efficiency is found when the salt concentration is low.
 
-    It is clear from the literature that there is significant progress to be made with respect to increasing the conversion efficiency.
+    It is clear from the literature that there is significant progress to be made with respect to increasing the conversion efficiency of streaming cells.
     Techniques to induce hydrodynamic slip at the fluid-solid interface are predicted to increase this efficiency to 30-40\%.~\cite{Davidson2008a, Ren2008a}
@@
     This type of enhancement would overcome the `no-slip boundary condition' at the solid-liquid interface.
-    Slip at the interface boundary would mean that ions in the Stern layer, where ionic concentration is highest, could also be moved through the channel.
+    Slip would mean that ions in the Stern layer, where ionic concentration is highest, could also be moved through the channel.
     Surface enhanced channels are out of the scope of this study due to cost and manufacturing difficulty.
@@
     Such a harvester must produce enough energy to operate a microprocessor and radio communication device.
-    It must collect all of its energy from a domestic water supply and be reliable.
+    It must collect all of its energy from a domestic water supply without being noticed and be reliable.
 
     The remainder of this work is presented as follows.
-    In section \ref{sect:streamingCell} we build, measure and calculate the conversion efficiency of a simple streaming potential cell.
-    We confirm the relationship between pressure and applied pressure and investigate the effect of channel height.
-    In section \ref{sect:waterConsumption} we estimate the amount of harvestable energy from a domestic water usage profile.
-    Section \ref{sect:powerRequirements} quantifies energy requirements of a simple electronic meter.
+    In section~\ref{sect:streamingCell} we build, measure and calculate the conversion efficiency of a simple streaming potential cell.
+    We confirm the relationship between voltage and applied pressure and investigate the effect of channel height.
+    In section~\ref{sect:waterConsumption} we estimate the amount of harvestable energy from a domestic water usage profile.
+    Section~\ref{sect:powerRequirements} quantifies energy requirements of a simple electronic meter reader with a wireless transmitter.
+    In section~\ref{sect:harvesterSize} we calculate the physical size of a harvester suitable for automatic meter reading.
     And finally, we conclude with a discussion on the feasibility of using streaming cells to harvest energy.
@@
     They glued plastic shims between parallel plates of glass, providing a simple way of setting a channel's height.
-    Using that method, the authors fabricated three cells with channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
-    Each of the channels were \SI{3}{\centi\metre} long and had a inner width of \SI{1}{\centi\metre}.
+    Using that method, the authors fabricated three cells with internal channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
+    Each of the channels were \SI{3}{\centi\metre} long and had a width of \SI{1}{\centi\metre}.
 
     We replicate the approximate dimensions of \cite{Gu2000} to produce ten streaming cells.
-    The approximate internal channel heights of these channels are \SI{245}{\micro\meter}, \SI{178}{\micro\meter}, \SI{161}{\micro\meter}, \SI{125}{\micro\meter}, \SI{106}{\micro\meter}, \SI{75}{\micro\meter}, \SI{71}{\micro\meter}, \SI{56}{\micro\meter}, \SI{52}{\micro\meter}, and \SI{26}{\micro\meter}.
+    The approximate internal heights of these channels are \SI{245}{\micro\metre}, \SI{178}{\micro\metre}, \SI{161}{\micro\metre}, \SI{125}{\micro\metre}, \SI{106}{\micro\metre}, \SI{75}{\micro\metre}, \SI{71}{\micro\metre}, \SI{56}{\micro\metre}, \SI{52}{\micro\metre}, and \SI{26}{\micro\metre}.
     The channels are made from glass microscope slides (Sail Brand - JIA 7101WT) sectioned into halves.
     Plastic shims (Garlock Colorplast) are epoxied (Selleys Araldite Ultra Clear Resin) between slide halves to separate the slides.
-    The dimensions at each end of each channel are measured under a microscope to determine the channel height once the channels had set.
+    The dimensions at each end of each channel are measured under a microscope to determine the channel height once the channels have set.
 
     Each channel is epoxied between two acrylic reservoirs and a base plate.
-    This provides a rigid structure under pressure and provides connection of wires and hoses.
-    Copper wires and silicon hoses are inserted into each reservoir to facilitate voltage measurement and the application of pressure.
+    This gives a rigid structure under pressure and allows the connection of copper wires and rubber hoses.
     A photo of one of the cells is shown in Fig. \ref{fig:cell}.
 
-    Pressure is applied to the cell by connection to tap and leaving the output connection open to atmosphere.
+    Pressure is applied to the cell by applying mains water pressure to one end while leaving the the other open to atmosphere.
     A Honeywell pressure sensor (model 26PC15SMT) is placed across the cell to measure applied pressure.
-    An Agilent precision measurement mainframe (model E5270B) is used to measure streaming potential, streaming current and to read the pressure sensor's output.
-    The working fluid, being tap water, had a conductivity of \SI{183e-6}{\siemens\per\meter} as measured with an EDT Instruments RE 388Tx Conductivity Meter.
+    An Agilent precision measurement mainframe (model E5270B) is used to measure the streaming potential, streaming current and the pressure sensor's output.
+    The working fluid, being tap water, had a conductivity of \SI{183}{\micro\siemens\per\metre} as measured with an EDT Instruments RE 388Tx Conductivity Meter.
 
@@
     Three of the cells burst before flow measurements were obtained.
-    % The \SI{26}{\micro\meter} channel shows a much lower gradient due to . which we expect is a result of a reduced flow rate.
-    % The \SI{26}{\micro\meter} cell burst before we obtained flow rate measurements.
+    % The \SI{26}{\micro\metre} channel shows a much lower gradient due to . which we expect is a result of a reduced flow rate.
+    % The \SI{26}{\micro\metre} cell burst before we obtained flow rate measurements.
 
@@
         \end{center}
-        \caption{Measured voltage developed across the \SI{52}{\micro\meter} streaming cell as a function of the differential pressure across the cell.}
+        \caption{Measured voltage developed across the \SI{52}{\micro\metre} streaming cell as a function of the differential pressure across the cell.}
         \label{fig:cellVoltagePressure}
@@
 
-    We now measure available power output of the \SI{71}{\micro\meter} streaming cell.
+    We now measure available power output of the \SI{71}{\micro\metre} streaming cell.
     This cell was chosen as it remained mechanically robust and had good output characteristics.
-    We measure the streaming voltage and pressure while sweeping the electrical current draw from the device.
+    We measure the streaming voltage and pressure while sweeping the electrical current drawn from the device.
     The applied pressure was held at \SI{260}{\kilo\pascal} for the duration of the measurement and the flow rate was previously determined to be \SI{2.05}{\milli\litre\per\second}.
 
-    Fig.~\ref{fig:cellOutput} shows the measured data along with the calculated power curve.
+    Fig.~\ref{fig:cellOutput} shows the measured data along with the calculated power.
     Using the power curve we calculate the cell's internal electrical resistance to be \SI{5.6}{\mega\ohm}.
@@
     Based on the pressure applied and the flow rate through the cell, the input power is \SI{539}{\milli\watt}.
-    Energy conversion efficiency is in the order of $1\times 10^{-6}\%$.
+    Energy conversion efficiency is in the order of \SI{1}{\micro\percent}.
+    While the conversion efficiency is much lower than those stated in the introduction, we use much larger channel dimensions and tap water as our working fluid.
 
@@
 
-    % Based on measurements of the \SI{52i}{\micro\meter} channel we estimate the amount of electrical power available for harvesting.
+    % Based on measurements of the \SI{52i}{\micro\metre} channel we estimate the amount of electrical power available for harvesting.
     % Fig.~\ref{fig:equivalentCircuit} shows the equivalent circuit for a streaming potential cell delivering a streaming current ($I_{S}$).
@@
     %     \end{center}
-    %     \caption{Maximum power available to an external load placed across the \SI{52}{\micro\meter} cell as a function of pressure differential.
+    %     \caption{Maximum power available to an external load placed across the \SI{52}{\micro\metre} cell as a function of pressure differential.
 Power has been calculated using a load resistance of \SI{30}{\giga\ohm} where only half of total power is available to the load.
@@
     Together these account for over three quarters of the indoor water usage in the average home.
-    We have created a flow profile from which to calculate the available harvestable energy using data from both \cite{Heinrich2008} and \cite{Heinrich2007}.
+
+    We have created a flow profile, using data from both \cite{Heinrich2008} and \cite{Heinrich2007}, from which to calculate the available energy.
     The profile fits the usage statistics of a home with two occupants according to the previously mentioned reports over the duration of a week.
-    The during that time five uses of a washing machine, fourteen showers and fifty six toilet flushes occur.
+    During that time five uses of a washing machine, fourteen showers and fifty six toilet flushes occur.
     A sample of the usage profiles of each item is shown in Fig. \ref{fig:profileSample}.
@@
     Figure~\ref{fig:headloss} shows the pressure head loss curve from a water meter typically installed at New Zealand homes (Kent PSMT 25mm).~\cite{WatercareNewZealand2014}
-    Using this curve we calculate power dissipation in a water meter during a washing machine cycle, shower, and toilet flush; presented as Fig.~\ref{fig:powerDissipated_meter}
+    Using this curve we calculate power dissipation in a water meter during a washing machine cycle, shower, and toilet flush; presented as Fig.~\ref{fig:powerDissipated_meter}.
     The total energy dissipated within the meter for each events is:
@@
     \item Execute 1 000 000 instructions (\SI{1.14}{\milli\joule})
-    \item Transmit 100 bytes of data over zigbee radio (\SI{12.3}{\milli\joule})
+    \item Transmit 100 bytes of data over ZigBee radio (\SI{12.3}{\milli\joule})
     \item Write 10 bytes to non-volatile memory (\SI{394}{\micro\joule})
@@
 
-    The energy requirements for a 100 byte data transmission over ZigBee (Digi International XBee S2) is presented as Fig.~\ref{fig:xbeePower} (recorded using a Tektronix TDC 2012 Digital Storage Oscilloscope across a \SI{10.2}{\ohm} current sense resistor).
+    The energy requirements for a 100 byte data transmission over ZigBee (Digi International XBee S2) is presented as Fig.~\ref{fig:xbeePower}.
+    This trace was recorded using a Tektronix TDC 2012 Digital Storage Oscilloscope across a \SI{10.2}{\ohm} current sense resistor.
 
@@
 
-    % \section{Estimation of Streaming Cell Harvester}
-    % \label{sect:harvesterSize}
+    \section{Sizing of Streaming Cell Harvester}
+    \label{sect:harvesterSize}
+    We now estimate the physical size of a harvester capable of supplying the energy to run a wireless water meter.
+    Auckland tap water has a sodium content of 2.1--26.0\thinspace mg/L.~\cite{WatercareNewZealand2012}
+    This equates to a Debye length in the range 0.3--\SI{1.0}{\nano\metre} and therefore the optimum channel height between 0.6--\SI{2.1}{\nano\metre}.
+    We envision a harvester made from stacked layers of glass, each layer forming a rectangular channel similar to those constructed earlier.
+
+    Such a harvester would be installed as shown in Fig.~\ref{fig:harvester} to control the pressure loss within the harvester.
+    Using the head loss curve from Fig.~\ref{fig:headloss}, a flow rate of \SI{7.50}{\litre\per\minute} would produce a pressure differential of \SI{4.5}{\kilo\pascal}.
+    Fig.~\ref{fig:cellVoltagePressure} confirms that the harvester output is linearly proportional to the pressure applied.
+
+    We know from Sections~\ref{sect:waterConsumption} and \ref{sect:powerRequirements} that an average of \SI{1}{\kilo\joule} per day is dissipated inside a water meter and that we need to harvest \SI{10}{\joule} for the electronic meter.
+    This equates to a efficiency target of 1\%.
+
+    We know from Section~\ref{sect:waterConsumption} that a typical shower consumes \SI{7.50}{\litre\per\minute} for approximately \SI{396}{\second}, dissipating a total of \SI{222}{\joule} of energy inside a water meter.
+    This equates to a power dissipation of \SI{560}{\milli\watt}.
+
+    This means our harvester must be capable of harvesting at least \SI{5.6}{\milli\watt} for a water flow rate of \SI{7.50}{\litre\per\minute}.
+
+    From the dimensions of the cell constructed and measured in Section~\ref{sect:streamingCell} we can expect \SI{152}{\nano\watt\per\metre} of channel width.
+    We assume here that doubling the width of a channel will double the output power of the channel.
+
+    To increase the efficiency of the channel the internal height needs to be reduced by a factor of \SI{52 600}, from \SI{71}{\micro\metre} to \SI{1.35}{\nano\metre} (the midpoint between \SI{0.6}{\nano\metre} and \SI{2.1}{\nano\metre}).
+    Doing so decreases the normalised output power of the streaming cell to \SI{2.89}{\pico\watt\per\metre}.
+    Therefore the width of a channel required to generate the target \SI{5.6}{\milli\watt} is \SI{1.94}{\giga\metre}.
+
+    Building such a device could be achieved by stacking \SI{1970000} glass channels, each of width \SI{984}{\metre} and thickness \SI{500}{\micro\metre}, creating a harvester that is \SI{984}{\square\metre} in size.
+    Keeping the channel length at \SI{1}{\centi\meter}, it may be possible to fit the required channels into a \SI{22.0}{\cubic\meter} volume.
+
+    \begin{figure}
+        \begin{center}
+        \includegraphics[]{harvester}
+        \end{center}
+        \caption{Harvester schematic for the streaming cell harvester.
+        Most water would bypass the harvester to prevent excessive pressure loss to the consumer.
+        An orifice plate is inserted into the bypass to increase the pressure differential across the harvester.}
+        \label{fig:harvester}
+    \end{figure}
 
@@
     \label{sect:conclusion}
-    We have calculated approximately \SI{1}{\kilo\joule} of energy is dissipated per day inside a typical water meter at a two occupant dwelling.
-    We have estimated that a harvester would need to harvest approximately \SI{10}{\joule} of energy per day to record and transmit water consumption data.
-    Therefore an energy harvester with an energy conversion efficiency of 1\% is required.
-    Streaming cells we constructed produced conversion efficiencies in the order of $1\times 10^{-6}\%$.
+    Approximately 100 times the required power to operate an automatic meter reader and transmitter is already dissipated inside today's mechanical water meters.
+    The streaming cells we constructed produced conversion efficiencies in the order of \SI{1}{\micro\percent}.
+    Scaling of these streaming cells to create a viable harvester would result in a \SI{22}{\cubic\metre} volume of glass with a mass of \SI{54}{\mega\gram}.
+    This is far from being a practical solution to the battery operated devices currently in use.
+    Theoretical methods proposed in the literature to increase the efficiency of streaming cells would reduce the figures presented.
+    Regardless of the efficiency of the cells, it is expected that such narrow openings in domestic water feeds will eventually become clogged.
+    It is our conclusion that energy harvesting for the purpose of automatic meter reading using streaming cells is not a practical option.
+    Other methods of energy harvesting from water flow should produce favourable results based on the abundance of available energy.
 
-    % \section{Conclusion}
     \bibliographystyle{plain}

### 2014-10-06 paper.tex
Final edits final

@@
 \usepackage{siunitx}
-\usepackage[dvipsnames]{color}
 
@@
     \label{sect:conclusion}
-    Approximately 100 times the required power to operate an automatic meter reader and transmitter is already dissipated inside today's mechanical water meters.
+    Approximately $100\times$ the required power to operate an automatic meter reader and transmitter is already dissipated inside today's mechanical water meters.
     The streaming cells we constructed produced conversion efficiencies in the order of \SI{1}{\micro\percent}.
@@
     This is far from being a practical solution to the battery operated devices currently in use.
+
     Theoretical methods proposed in the literature to increase the efficiency of streaming cells would reduce the figures presented.
     Regardless of the efficiency of the cells, it is expected that such narrow openings in domestic water feeds will eventually become clogged.
-    It is our conclusion that energy harvesting for the purpose of automatic meter reading using streaming cells is not a practical option.
-    Other methods of energy harvesting from water flow should produce favourable results based on the abundance of available energy.
 
-    \bibliographystyle{plain}
+    It is our conclusion that energy harvesting using streaming cells for the purpose of automatic meter reading is not practical.
+    Other methods of energy harvesting from water flow should produce favourable results.
+    This is based on the quantity of energy already dissipated within today's mechanical meters.
+    \bibliographystyle{ieeetr}
     \bibliography{library}

### 2014-10-14 paper.tex
Kyle's proofread

@@
 
-    Figure~\ref{fig:headloss} shows the pressure head loss curve from a water meter typically installed at New Zealand homes (Kent PSMT 25mm).~\cite{WatercareNewZealand2014}
+    Figure~\ref{fig:headloss} shows the pressure head loss curve from a water meter typically installed at New Zealand homes (Kent PSMT \SI{25}{\milli\meter}).~\cite{WatercareNewZealand2014}
     Using this curve we calculate power dissipation in a water meter during a washing machine cycle, shower, and toilet flush; presented as Fig.~\ref{fig:powerDissipated_meter}.
@@
     \item Sleep for \SI{1}{\second} (\SI{97.4}{\nano\joule})
-    \item Execute 1 000 instructions (\SI{1.14}{\micro\joule})
+    \item Execute \SI{1000} instructions (\SI{1.14}{\micro\joule})
     \item Take 2 ADC measurements (\SI{2.56}{\nano\joule})
@@
     \begin{itemize}
-    \item Execute 1 000 000 instructions (\SI{1.14}{\milli\joule})
+    \item Execute \SI{1000000} instructions (\SI{1.14}{\milli\joule})
     \item Transmit 100 bytes of data over ZigBee radio (\SI{12.3}{\milli\joule})
@@
 
-    To increase the efficiency of the channel the internal height needs to be reduced by a factor of \SI{52 600}, from \SI{71}{\micro\metre} to \SI{1.35}{\nano\metre} (the midpoint between \SI{0.6}{\nano\metre} and \SI{2.1}{\nano\metre}).
+    To increase the efficiency of the channel the internal height needs to be reduced by a factor of \SI{52600}, from \SI{71}{\micro\metre} to \SI{1.35}{\nano\metre} (the midpoint between \SI{0.6}{\nano\metre} and \SI{2.1}{\nano\metre}).
     Doing so decreases the normalised output power of the streaming cell to \SI{2.89}{\pico\watt\per\metre}.
@@
     \label{sect:conclusion}
-    Approximately $100\times$ the required power to operate an automatic meter reader and transmitter is already dissipated inside today's mechanical water meters.
+    Approximately one hundred times the required power to operate an automatic meter reader and transmitter is already dissipated inside today's mechanical water meters.
     The streaming cells we constructed produced conversion efficiencies in the order of \SI{1}{\micro\percent}.

### 2014-10-14 paper.tex
Removed test

@@
         \end{center}
-        \caption{One of our ten constructed streaming cells mounted in an acrylic holder.
+        \caption{One of ten constructed streaming cells mounted in an acrylic holder.
 Copper wires have been epoxied into each side to provide a means of measuring the developed potential across the cell.
@@
     Our estimation shows a monitoring and transmitting device would need about \SI{6.96}{\joule} per day to operate in ideal transmission conditions.
-    If the transmitter were to require $100\times$ more energy to transmit, as an estimate of poor conditions, the energy requirements would jump to \SI{9.39}{\joule} per day.
+    If the transmitter were to require a hundred times more energy to transmit, as an estimate of poor conditions, the energy requirements would jump to \SI{9.39}{\joule} per day.
     It is therefore estimated that an energy harvester would need to deliver approximately \SI{10}{\joule} of energy per day.
@@
     We now estimate the physical size of a harvester capable of supplying the energy to run a wireless water meter.
-    Auckland tap water has a sodium content of 2.1--26.0\thinspace mg/L.~\cite{WatercareNewZealand2012}
+    Auckland tap water has a sodium content of 2.1--\SI{26.0}{\milli\gram\per\litre}.~\cite{WatercareNewZealand2012}
     This equates to a Debye length in the range 0.3--\SI{1.0}{\nano\metre} and therefore the optimum channel height between 0.6--\SI{2.1}{\nano\metre}.

### 2014-11-11 paper.tex
Updated for final submission to ENZcon

--- 2014-10-06 paper.tex
@@
 \usepackage{siunitx}
+\usepackage{cite}
 
@@
 
-    A double layer is comprised of two individual layers; the Stern and diffuse layers.
-    The Stern layer refers to immobilised counter-ions bound directly to the liquid-solid interface.~\cite{Salieb-Beugelaar2009}
-    The diffuse layer surrounds the Stern layer and contains counter-ions that are not so strongly bound as to be immobile.
-    The thickness of the double layer is defined as the Debye length ($l_{D}$) and is dependant upon the ionic concentration of the liquid.~\cite{Israelachvili2011}
+    A double layer is comprised of two individual layers; the \emph{compact} and \emph{diffuse} layers.
+    The compact layer refers to immobilised counter-ions bound directly to the liquid-solid interface.~\cite{Salieb-Beugelaar2009}
+    The diffuse layer surrounds the compact layer and contains counter-ions that are not so strongly bound as to be immobile.
+    The thickness of the double layer is defined as the Debye length ($l_{D}$) and is dependant upon the ionic concentration of the liquid and the electric potential on the solid surface.~\cite{Israelachvili2011}
     When the dimensions of a streaming cell channel become small enough, double layers will overlap.
@@
 
-    Channels can be created individually using a range fabrication methods, such as chemical etching or using narrowly separated parallel plates.
+    Channels can be created individually using a range of fabrication methods, such as chemical etching or using narrowly separated parallel plates.
     They can also be formed en-mass by using porous materials such as glass or ceramics, where the pores themselves act as channels.
@@
         \item 0.8\% by forcing pure water through a ceramic rod populated with \SI{6}{\micro\metre} pores.~\cite{Yang2004}
-        \item 3\% by forcing sodium chloride solution through a \SI{75}{\nano\metre} by \SI{50}{\micro\metre} silica channel.~\cite{Heyden2007}
-        \item 0.77\% by forcing sodium chloride through a \SI{200}{\nano\metre} pore in an alumina membrane.~\cite{Lu2006}
-        \item 5\% by forcing sodium chloride solution through a \SI{0.5}{\nano\metre} cylindrical pore in polyethylene terephalate foil.~\cite{Xie2008}
+        \item 3\% by forcing a sodium chloride solution through a \SI{75}{\nano\metre} by \SI{50}{\micro\metre} silica channel.~\cite{Heyden2007}
+        \item 0.77\% by forcing a sodium chloride solution through a \SI{200}{\nano\metre} pore in an alumina membrane.~\cite{Lu2006}
+        \item 5\% by forcing a sodium chloride solution through a \SI{0.5}{\nano\metre} cylindrical pore in polyethylene terephalate foil.~\cite{Xie2008}
     \end{itemize}
@@
     This type of enhancement would overcome the `no-slip boundary condition' at the solid-liquid interface.
-    Slip would mean that ions in the Stern layer, where ionic concentration is highest, could also be moved through the channel.
+    Slip would mean that ions in the compact layer, where ionic concentration is highest, could also be moved through the channel.
     Surface enhanced channels are out of the scope of this study due to cost and manufacturing difficulty.
@@
     Such a harvester must produce enough energy to operate a microprocessor and radio communication device.
-    It must collect all of its energy from a domestic water supply without being noticed and be reliable.
+    It must collect all of its energy from a domestic water supply without noticeably affecting the supply, and be reliable.
 
     The remainder of this work is presented as follows.
-    In section~\ref{sect:streamingCell} we build, measure and calculate the conversion efficiency of a simple streaming potential cell.
+    In section~\ref{sect:streamingCell} we build, measure, and calculate the conversion efficiency of a simple streaming potential cell.
     We confirm the relationship between voltage and applied pressure and investigate the effect of channel height.
@@
     Plastic shims (Garlock Colorplast) are epoxied (Selleys Araldite Ultra Clear Resin) between slide halves to separate the slides.
-    The dimensions at each end of each channel are measured under a microscope to determine the channel height once the channels have set.
+    The dimensions at each end of each channel are measured under a microscope to determine the channel height once the epoxy resin has set.
 
-    Each channel is epoxied between two acrylic reservoirs and a base plate.
+    Each channel is then epoxied between two acrylic reservoirs and a base plate.
     This gives a rigid structure under pressure and allows the connection of copper wires and rubber hoses.
@@
     Spread in the data is attributed to uncertainty in the internal dimensions of each cell.
-    Due to the opacity of the resin used, measurement of the internal cell dimensions was not possible.
+    Due to the opacity of the resin used, measurement of the internal cell widths was not possible.
     The plot shows the relationship between channel height and voltage gradient per Pascal of applied pressure.
-    Each cell had a different flow rate, which this plot does not take into account.
-    Three of the cells burst before flow measurements were obtained.
+    Each cell also had a different flow rate, which this plot does not take into account.
+    Unfortunately, three of the cells burst before flow measurements could be obtained.
     % The \SI{26}{\micro\metre} channel shows a much lower gradient due to . which we expect is a result of a reduced flow rate.
@@
 
-    Figure~\ref{fig:headloss} shows the pressure head loss curve from a water meter typically installed at New Zealand homes (Kent PSMT 25mm).~\cite{WatercareNewZealand2014}
+    Fig.~\ref{fig:headloss} shows the pressure head loss curve from a water meter typically installed at New Zealand homes (Kent PSMT 25mm).~\cite{WatercareNewZealand2014}
     Using this curve we calculate power dissipation in a water meter during a washing machine cycle, shower, and toilet flush; presented as Fig.~\ref{fig:powerDissipated_meter}.
@@
     % These figures are based on average duration and flow rates as found in \cite{Heinrich2008}, and the estimated head loss from Fig.~\ref{fig:headloss}.
-    Over an average week the the reference water meter would dissipate approximately \SI{7.20}{\kilo\joule} of energy; averaging \SI{1.03}{\kilo\joule} per day.
+    Over an average week the reference water meter would dissipate approximately \SI{7.20}{\kilo\joule} of energy; averaging \SI{1.03}{\kilo\joule} per day.
 
@@
     Our estimation shows a monitoring and transmitting device would need about \SI{6.96}{\joule} per day to operate in ideal transmission conditions.
-    If the transmitter were to require $100\times$ more energy to transmit, as an estimate of poor conditions, the energy requirements would jump to \SI{9.39}{\joule} per day.
+    If the transmitter were to require one hundred times more energy to transmit, as an estimate of poor conditions, the energy requirements would jump to \SI{9.39}{\joule} per day.
     It is therefore estimated that an energy harvester would need to deliver approximately \SI{10}{\joule} of energy per day.
@@
         \begin{center}
-        \includegraphics[]{harvester}
+        \includegraphics[]{harvester2}
         \end{center}
@@
     It is our conclusion that energy harvesting using streaming cells for the purpose of automatic meter reading is not practical.
-    Other methods of energy harvesting from water flow should produce favourable results.
-    This is based on the quantity of energy already dissipated within today's mechanical meters.
+    Based on the quantity of energy already dissipated within mechanical meters, other methods of energy harvesting from water flow should produce favourable results.
     \bibliographystyle{ieeetr}

### 2014-11-17 paper.tex
Fixed wrong calculations

@@
 
-    Building such a device could be achieved by stacking \SI{1970000} glass channels, each of width \SI{984}{\metre} and thickness \SI{500}{\micro\metre}, creating a harvester that is \SI{984}{\square\metre} in size.
-    Keeping the channel length at \SI{1}{\centi\meter}, it may be possible to fit the required channels into a \SI{22.0}{\cubic\meter} volume.
+    Building such a device could be achieved by stacking \SI{1970000} glass channels, each of width \SI{984}{\metre} and thickness \SI{500}{\micro\metre}, creating a harvester that is \SI{968}{\square\kilo\metre} in size.
+    Keeping the channel length at \SI{1}{\centi\meter}, it may be possible to fit the required channels into a \SI{9.68}{\cubic\kilo\meter} volume.
 
@@
         \begin{center}
-        \includegraphics[]{harvester2}
+        \includegraphics[]{harvester3}
         \end{center}
@@
     \label{sect:conclusion}
-    Approximately one hundred times the required power to operate an automatic meter reader and transmitter is already dissipated inside today's mechanical water meters.
+    Approximately one hundred times the required power to operate an automatic meter reader and transmitter is lost in current mechanical water meters.
     The streaming cells we constructed produced conversion efficiencies in the order of \SI{1}{\micro\percent}.
-    Scaling of these streaming cells to create a viable harvester would result in a \SI{22}{\cubic\metre} volume of glass with a mass of \SI{54}{\mega\gram}.
+    Scaling these cells to create a viable harvester would result in a \SI{9.68}{\cubic\kilo\metre} volume of glass with a mass of \SI{24.4}{\giga\gram}.
     This is far from being a practical solution to the battery operated devices currently in use.
 
-    Theoretical methods proposed in the literature to increase the efficiency of streaming cells would reduce the figures presented.
-    Regardless of the efficiency of the cells, it is expected that such narrow openings in domestic water feeds will eventually become clogged.
+    Theoretical methods proposed in the literature to increase the efficiency of streaming cells would reduce these figures.
+    Regardless of efficiency, it is expected that such narrow openings in domestic water feeds will eventually become clogged.
 
     It is our conclusion that energy harvesting using streaming cells for the purpose of automatic meter reading is not practical.
-    Based on the quantity of energy already dissipated within mechanical meters, other methods of energy harvesting from water flow should produce favourable results.
+    Based on the quantity of energy already dissipated within mechanical meters, other methods of energy harvesting should produce favourable results.
     \bibliographystyle{ieeetr}

### 2014-11-24 paper.tex
Final submission

@@
 
-\title{Feasibility of Harvesting Power To Run A Domestic Water Meter Using Streaming Cell Technology}
+\title{Feasibility of Harvesting Power to Run a Domestic Water Meter Using Streaming Cell Technology}
 
@@
         Section~\ref{sect:powerRequirements} quantifies energy requirements of a simple electronic meter reader with a wireless transmitter.
-    In section~\ref{sect:harvesterSize} we calculate the physical size of a harvester suitable for automatic meter reading.
+        In section~\ref{sect:harvesterSize} we calculate the physical size of a harvester intended for electronic meter reading.
         And finally, we conclude with a discussion on the feasibility of using streaming cells to harvest energy.
@@
         Using that method, the authors fabricated three cells with internal channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
-    Each of the channels were \SI{3}{\centi\metre} long and had a width of \SI{1}{\centi\metre}.
+        Each of the channels were \SI{3}{\centi\metre} long and had an internal width of \SI{1}{\centi\metre}.
 
@@
 
-    Based on the pressure applied and the flow rate through the cell, the input power is \SI{539}{\milli\watt}.
-    Energy conversion efficiency is in the order of \SI{1}{\micro\percent}.
-    While the conversion efficiency is much lower than those stated in the introduction, we use much larger channel dimensions and tap water as our working fluid.
+        By calculating the power provided to the harvester and knowing the power output we calculate the cell efficiency.
+
+        % \begin{equation}
+        %     P_{in} = \SI{260}{kPa} \cdot 2.05\times10^{-6} \frac{m^{3}}{s} = \SI{533}{mW}
+        % \end{equation}
+        % \begin{equation}
+        %     P_{out} = \SI{1.53}{\nano\watt}
+        % \end{equation}
+        % \begin{equation}
+        %     \epsilon = \frac{P_{out}}{P_{in}} = 2.87\times 10^{-9} = 0.287\thinspace\mu\%
+        % \end{equation}
+
+        \begin{eqnarray}
+            P_{in} =& \SI{260}{kPa} \cdot \SI{2.05e-6}{\cubic\meter\per\second} = \SI{533}{mW}\\
+            P_{out} =& \SI{1.53}{\nano\watt}\\
+            \epsilon =& \frac{P_{out}}{P_{in}} = 2.87\times 10^{-9} = 0.287\thinspace\mu\%
+        \end{eqnarray}
+
+        Energy conversion efficiency is in the order of \SI{0.3}{\micro\percent}.
+        While the conversion efficiency is much lower than those stated in the introduction, we use much larger channel dimensions.
 
@@
         \label{sect:harvesterSize}
-    We now estimate the physical size of a harvester capable of supplying the energy to run a wireless water meter.
-    Auckland tap water has a sodium content of 2.1--\SI{26.0}{\milli\gram\per\litre}.~\cite{WatercareNewZealand2012}
-    This equates to a Debye length in the range 0.3--\SI{1.0}{\nano\metre} and therefore the optimum channel height between 0.6--\SI{2.1}{\nano\metre}.
+        We now estimate the physical size of a harvester capable of supplying enough energy to run an electronic water meter.
         We envision a harvester made from stacked layers of glass, each layer forming a rectangular channel similar to those constructed earlier.
-
-    Such a harvester would be installed as shown in Fig.~\ref{fig:harvester} to control the pressure loss within the harvester.
-    Using the head loss curve from Fig.~\ref{fig:headloss}, a flow rate of \SI{7.50}{\litre\per\minute} would produce a pressure differential of \SI{4.5}{\kilo\pascal}.
-    Fig.~\ref{fig:cellVoltagePressure} confirms that the harvester output is linearly proportional to the pressure applied.
+        Such a harvester would be installed as shown in Fig.~\ref{fig:harvester} to control the pressure loss within the harvester and to the consumer.
 
@@
 
-    We know from Section~\ref{sect:waterConsumption} that a typical shower consumes \SI{7.50}{\litre\per\minute} for approximately \SI{396}{\second}, dissipating a total of \SI{222}{\joule} of energy inside a water meter.
-    This equates to a power dissipation of \SI{560}{\milli\watt}.
+        Auckland tap water has a sodium content of 2.1--\SI{26.0}{\milli\gram\per\litre}.~\cite{WatercareNewZealand2012}
+        This equates to a Debye length in the range 0.3--\SI{1.0}{\nano\metre} and therefore the optimum channel height between 0.6--\SI{2.1}{\nano\metre}.
 
-    This means our harvester must be capable of harvesting at least \SI{5.6}{\milli\watt} for a water flow rate of \SI{7.50}{\litre\per\minute}.
+        We know from Section~\ref{sect:waterConsumption} that a typical shower consumes \SI{7.50}{\litre\per\minute} for approximately \SI{396}{\second}.
+        Using the head loss curve from Fig.~\ref{fig:headloss}, a flow rate of \SI{7.50}{\litre\per\minute} would produce a pressure differential of \SI{4.48}{\kilo\pascal}.
+        Therefore, a mechanical water meter dissipates a total of \SI{222}{\joule} at a rate of \SI{560}{\milli\watt} within the meter during a typical shower.
 
-    From the dimensions of the cell constructed and measured in Section~\ref{sect:streamingCell} we can expect \SI{152}{\nano\watt\per\metre} of channel width.
+        This means a harvester must be capable of harvesting at least \SI{5.60}{\milli\watt} at a pressure differential of \SI{4.48}{\kilo\pascal}.
+        From the dimensions of the cell constructed and measured in Section~\ref{sect:streamingCell} we can expect \SI{153}{\nano\watt\per\metre} of channel width at a pressure of \SI{260}{\kilo\pascal}.
+        Fig.~\ref{fig:cellVoltagePressure} confirms that the harvester output is linearly proportional to the pressure applied.
         We assume here that doubling the width of a channel will double the output power of the channel.
 
-    To increase the efficiency of the channel the internal height needs to be reduced by a factor of \SI{52600}, from \SI{71}{\micro\metre} to \SI{1.35}{\nano\metre} (the midpoint between \SI{0.6}{\nano\metre} and \SI{2.1}{\nano\metre}).
-    Doing so decreases the normalised output power of the streaming cell to \SI{2.89}{\pico\watt\per\metre}.
-    Therefore the width of a channel required to generate the target \SI{5.6}{\milli\watt} is \SI{1.94}{\giga\metre}.
+        Normalising the cell's output for width and pressure yields \SI{588}{\pico\watt\per\meter\per\kilo\pascal}.
+        Therefore at our target pressure of \SI{4.48}{\kilo\pascal} we can expect output of \SI{2.64}{\nano\watt\per\meter}.
+        Dividing the target output of \SI{5.60}{\milli\watt} by this figure yields a required width of \SI{2.12e6}{\meter}.
+        This equates to a harvester that, when packed into a cube, would have sides of \SI{3.17}{\meter} in length.
 
-    Building such a device could be achieved by stacking \SI{1970000} glass channels, each of width \SI{984}{\metre} and thickness \SI{500}{\micro\metre}, creating a harvester that is \SI{968}{\square\kilo\metre} in size.
-    Keeping the channel length at \SI{1}{\centi\meter}, it may be possible to fit the required channels into a \SI{9.68}{\cubic\kilo\meter} volume.
+        % Setting the glass substrate at thickness \SI{500}{\micro\meter}, and using a channel depth of \SI{3.00}{\centi\meter}, this length can reduced by stacking sections of channels.
+        % Stacking these cells on top of and behind each other would then result in a cube having sides of \SI{3.17}{\meter}.
+        % This cube would be capable of powering the electronic water meter with a pressure differential of \SI{4.48}{\kilo\pascal}.
+        % That pressure differential would be unobtainable using a domestic feed across a channel with those dimensions.
+
+        % Now we consider a harvester with internal channel height of \SI{1.35}{\nano\metre}.
+        % We have chosen this dimension as it is the midpoint between \SI{0.6}{\nano\metre} and \SI{2.1}{\nano\metre}, the optimum channel height for the conductivity of tap water.
+        % At this dimension we would hope for a conversion efficiency of 1\%, half the theoretically predicted 2\%.
+
+        % Increasing the channel's efficiency to 1\% puts its output at \SI{2.05}{\milli\watt\per\meter\per\kilo\pascal}.
+        % However, reducing the channel height from \SI{75}{\micro\meter} to \SI{1.00}{\nano\meter} while preserving channel cross-section drops the power-per-width down to \SI{27.3}{\nano\watt\per\meter\per\kilo\pascal}.
+        % At the target pressure of \SI{4.48}{\kilo\pascal} this delivers \SI{122}{\nano\watt\per\meter}.
+        % To get \SI{5.60}{\milli\watt} would require a \SI{45.7}{\kilo\meter} wide channel.
+        % Again stacking and packing the channels into a cube, the harvester would occupy a \SI{0.229}{\cubic\meter} volume.
+        % This is equivalent to a cube having sides of \SI{62}{\centi\meter}.
+
+        % To increase the efficiency of the channel the internal height needs to be reduced by a factor of \SI{52600}, from \SI{71}{\micro\metre} to \SI{1.35}{\nano\metre} (the midpoint between \SI{0.6}{\nano\metre} and \SI{2.1}{\nano\metre}).
+        % Doing so decreases the normalised output power of the streaming cell to \SI{2.89}{\pico\watt\per\metre}.
+        % Therefore the width of a channel required to generate the target \SI{5.6}{\milli\watt} is \SI{1.94}{\giga\metre}.
+
+        % Building such a device could be achieved by stacking \SI{1970000} glass channels, each of width \SI{984}{\metre} and thickness \SI{500}{\micro\metre}, creating a harvester that is \SI{0.968}{\square\kilo\metre} in size.
+        % Keeping the channel length at \SI{1}{\centi\meter}, it may be possible to fit the required channels into a \SI{9680}{\cubic\meter} volume.
 
@@
         \label{sect:conclusion}
-    Approximately one hundred times the required power to operate an automatic meter reader and transmitter is lost in current mechanical water meters.
-    The streaming cells we constructed produced conversion efficiencies in the order of \SI{1}{\micro\percent}.
-    Scaling these cells to create a viable harvester would result in a \SI{9.68}{\cubic\kilo\metre} volume of glass with a mass of \SI{24.4}{\giga\gram}.
-    This is far from being a practical solution to the battery operated devices currently in use.
+        The streaming cells fabricated in this paper achieved a conversion efficiency of approximately \SI{0.3}{\micro\%}.
+        Stacking these cells into harvester capable of powering an electronic water meter would result in a cube having sides \SI{3.17}{\meter} in length.
 
-    Theoretical methods proposed in the literature to increase the efficiency of streaming cells would reduce these figures.
+        %Methods proposed to further increase the efficiency of streaming cell energy conversion would reduce this figure.
+        We have estimated that harvesting 1\% of the power dissipated in a mechanical water meter would be sufficient to power an electronic water meter.
+        In order to achieve this, such a cell would have to operate near the maximum predicted efficiency.
+        % A streaming cell harvester capable of achieving the target 1\% conversion efficiency would have to operate near the theoretical maximum predicted in the literature.
         Regardless of efficiency, it is expected that such narrow openings in domestic water feeds will eventually become clogged.
+        We conclude that energy harvesting using readily fabricated streaming cells for the purpose of electronic meter reading is not yet practical.
 
-    It is our conclusion that energy harvesting using streaming cells for the purpose of automatic meter reading is not practical.
-    Based on the quantity of energy already dissipated within mechanical meters, other methods of energy harvesting should produce favourable results.
+        Methods of inducing hydrodynamic slip at the interface may produce a more feasible streaming cell harvester design.
+        %We have estimated that harvesting 1\% of the power already lost inside a mechanical water meter would be sufficient to operate an electronic meter.
+
+        % Based on this figure, we suggest that other methods of energy harvesting should produce more viable results.
     \bibliographystyle{ieeetr}

### 2014-11-24 graphs.py

@@ -56,14 +56,14 @@ ys_flow_toilet_min = list(map(lambda x: x * 60.0, ys_toilet))
 ys_flow_washing_min = list(map(lambda x: x * 60.0, ys_washing))
 xs_flow_min = list(map(lambda x: x / 60.0, xs))
 
-ax = plt.gca()
-ax.set_xlabel('Time (minutes)')
-ax.set_ylabel('Flow (L/min)')
-ax.set_ylim(0,9)
-plt.plot(xs_flow_min,ys_flow_washing_min, label='Washing machine', linestyle='-')
-plt.plot(xs_flow_min,ys_flow_shower_min, label='Shower', linestyle='--')
-plt.plot(xs_flow_min,ys_flow_toilet_min, label='Toilet', linestyle=':')
-plt.legend(frameon=False, ncol=3)
+# ax = plt.gca()
+# ax.set_xlabel('Time (minutes)')
+# ax.set_ylabel('Flow (L/min)')
+# ax.set_ylim(0,9)
+# plt.plot(xs_flow_min,ys_flow_washing_min, label='Washing machine', linestyle='-')
+# plt.plot(xs_flow_min,ys_flow_shower_min, label='Shower', linestyle='--')
+# plt.plot(xs_flow_min,ys_flow_toilet_min, label='Toilet', linestyle=':')
+# plt.legend(frameon=False, ncol=3)
 
 # Cant put these on the same axis because the power output isnt linear with flow
 # ax2 = plt.gca().twinx()
@@ -72,7 +72,7 @@ plt.legend(frameon=False, ncol=3)
 # ax2.set_ylabel('Power available')
 
 
-plt.savefig('graph_profile.pdf', format='pdf')
+# plt.savefig('graph_profile.pdf', format='pdf')
 
 ## Calculate the amount of energy in each event
 
@@ -101,167 +101,168 @@ def flow_to_power(flow_litrePerSecond):
     flow_cubicMeterPerHour = convert_litrePerSecond_cubicMeterPerHour(flow_litrePerSecond)
     flow_cubicMeterPerSecond = convert_cubicMeterPerHour_cubicMeterPerSecond(flow_cubicMeterPerHour)
     pressure_MPa = pressure_loss_MPa(flow_cubicMeterPerHour)
+    print("Pressure drop = " + str(pressure_MPa * 1000))
     power_available = calc_power(convert_MPa_Pa(pressure_MPa), flow_cubicMeterPerSecond)
[…]

### 2015-12-20 paper.tex
Corrected units of conductivity

@@
         An Agilent precision measurement mainframe (model E5270B) is used to measure the streaming potential, streaming current and the pressure sensor's output.
-        The working fluid, being tap water, had a conductivity of \SI{183}{\micro\siemens\per\metre} as measured with an EDT Instruments RE 388Tx Conductivity Meter.
+        The working fluid, being tap water, had a conductivity of \SI{183}{\micro\siemens\per\centi\metre} as measured with an EDT Instruments RE 388Tx Conductivity Meter.
 
